---
title: A First Glance at nordatlantisk-ft
authors:
  - name: Moritz Twente
    affiliation: University of Basel
    email: moritz.twente@unibas.ch
    orcid: 0009-0005-7187-9774
date-modified: last-modified
bibliography: assets/nordatlantisk-ft.bib
link-citations: true
lang: en
---

```{r setup}
#| echo: false
#| message: false

# Setup -----
## Packages -----

library(here)
library(ggplot2)
library(dplyr)
library(readr)
library(knitr)
library(forcats)
library(lubridate)

## Read Data -----

### List of MPs -----
mp_names <- readRDS(here("data", "processed", "MP_names.rds"))

### List of political parties -----
political_parties <- read.csv(here("assets", "background_data", "political_parties.csv"), sep = ";", check.names = FALSE)

### Voting Records Database -----
northatlantic_ft <- readRDS(here("data", "processed", "northatlantic_ft.rds"))

plot_dataset <- northatlantic_ft %>%
  left_join(mp_names %>% select(surname, origin), by = "surname")

### Timeline of Mandates -----
mandates <- read.delim(here("assets", "background_data", "MP_dates.csv"), sep = ";", stringsAsFactors = FALSE)
elections <- read.delim(here("assets", "background_data", "election_dates.csv"), sep = ";", stringsAsFactors = FALSE)

#### Convert dates
mandates <- mandates %>%
  mutate(
    start = ymd(start),
    end   = ymd(end),
    # Replace NA in "end" with today's date
    end   = if_else(is.na(end), Sys.Date(), end)
  )

## Manipulate Data -----

### Subset only with votes that were actually cast
plot_dataset_without_absences <- subset(plot_dataset, vote_type_id != 3)

### Order dataset by MP surnames for plotting
plot_dataset_ordered <- plot_dataset %>%
  mutate(surname = fct_reorder(surname, vote_type_id, .fun = length))

## Set Plotting Theme -----

theme_nordatlantisk_basis <- function(){
  
  theme_grey() %+replace%
    theme(axis.title = element_blank(),
          axis.ticks.y = element_blank(),
          panel.background = element_blank(),
          panel.grid.major.x = element_line(color = "#000000", linewidth = 0.1),
          panel.grid.minor.x = element_line(color = "#000000", linewidth = 0.1),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.y = element_blank(),
          axis.ticks.x = element_line(color = "#000000", linewidth = 0.1),
          axis.line.y.left = element_line(color = "#000000", linewidth = 0.1))
}

```

There are 179 MPs in Folketinget, the parliament of Denmark. But only 175 of them are elected in Denmark proper, while the remaining four seats are guaranteed for the so-called North Atlantic MPs from Greenland and the Faroe Islands, which both are autonomous members of the Danish Realm today after being under Danish colonial rule for centuries.

## Dataset

*nordatlantisk-ft* is compiled from data available on Folketingets Open Data platform [@folketingetFolketingetsAbneData2025] and comprises voting records of Northatlantic MPs. This includes records of `r length(unique(northatlantic_ft$ballot_id))` ballots in Folketinget as per the last update (`r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`). See the [Codebook](docs/codebook.qmd) for details and refer to @berntzenParliamentaryOpenData2019 for background information on Folketingets open data ecosystem.

## MPs

This dataset contains votes cast by Greenlandic and Faroese MPs since `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")`. There have been `r nrow(mp_names)` individual politicians from Greenland or the Faroe Islands who served as MPs in the time frame covered by Folketinget's Open Data Platform (@tbl-MPs). `r sum(mp_names$origin == "GL")` of them are members of Greenlandic parties, and `r sum(mp_names$origin == "FO")` are representing Faroese parties. See @harderSupplerendeMaterialeFaeroske2022 for a list of all Greenlandic and Faroese MPs and their party association(s) going back until 1953.

```{r mp-list}
#| echo: false
#| message: false
#| label: tbl-MPs
#| tbl-cap: List of MPs from Greenland and the Faroe Islands in Folketinget since 2004.

MPs_gl <- mp_names %>%
  filter(origin == "GL") %>%
  select(-origin, -start_date, -end_date) %>%
  arrange(surname)

MPs_fo <- mp_names %>%
  filter(origin == "FO") %>%
  select(-origin, -start_date, -end_date) %>%
  arrange(surname)

kable(MPs_gl, caption = "MPs from Greenlandic Parties")
kable(MPs_fo, caption = "MPs from Faroese Parties")
```

As documented in the column `substitute`, some of the politicians that are part of this data set joined Folketinget in the role of a substitute member[^1], filling in for the originally elected MPs while they were on leave [cf. @harderFaeroskeOgGronlandske2022, 12-13]. @fig-mandates shows membership periods and substitions on a timeline for the duration that is covered by this data set[^2].

[^1]: Doris Jakobsen (SIU), Magni Arge (E) and Sjúrður Skaale (C) all first became MPs as substitute members, but later joined as regular MPs after a general election. For now, they are listed as full members in this dataset.

[^2]: An earlier term served by Edmund Joensen is cut off from the timeline since there are no voting records available online earlier than `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")`.

```{r timeline-mandates}
#| echo: false
#| message: false
#| label: fig-mandates
#| fig-cap: Timeline of MPs from Greenland and the Faroe Islands during the timeframe covered by this data set.

# remove pre-2000 MPs (Edmund Joensen's first term)
mandates <- mandates %>%
  filter(end >= as.Date("2000-01-01"))

# Order MPs by first start date for nicer plotting
mandates <- mandates %>%
  group_by(surname) %>%
  mutate(first_start = min(start)) %>%
  ungroup() %>%
  arrange(desc(first_start)) %>%
  mutate(surname = factor(surname, levels = unique(surname)))

mandates$origin <- factor(mandates$origin, levels = c("GL", "FO"))

ggplot(mandates, aes(x = start, xend = end, y = surname, yend = surname, color = substitute)) +
  geom_segment(linewidth = 6, lineend = "butt") +
  scale_color_manual(values = c("FALSE" = "#6195CF", "TRUE" = "#F7CB45"), labels = c("Regular", "Substitute")) +
  labs(
    color = "Membership"
  ) +
  
  # Folketing Elections
  geom_vline(data = elections, aes(xintercept = as.Date(date), linetype = election),
    color = "#000000",
    linewidth = 0.2
  ) +
  scale_linetype_manual(values = c("General Election" = "longdash"), name = "") +
  
  facet_grid(origin ~ ., scales = "free_y", space = "free_y",
             labeller = labeller(origin = c("GL" = "Greenland", "FO" = "Faroe Islands"))
  ) +
  
  coord_cartesian(xlim = c(min(northatlantic_ft$ballot_date), NA)) +
  
  theme_nordatlantisk_basis() +
  theme(legend.position = "right",
        panel.grid.major.y = element_line(color = "#777777", linewidth = 0.05),
        panel.grid.minor.x = element_blank())
```

## Political Parties

Since 2004, MPs from the Faroe Islands were members of `r sum(political_parties$Origin == "FO")` different political parties. Voters in Greenland elected politicians from `r sum(political_parties$Origin == "GL") - 2` different political parties. However, two of the Greenlandic representatives -- Aleqa Hammond and Aki-Matilda Høegh-Dam -- switched party affiliation during their time as member of Folketinget and joined two relatively young parties (Nunatta Qitornai and Naleraq[^3]).

[^3]: Both parties have been formed quite recently -- Naleraq in 2014 and Nunatta Qitornai in 2017. See @ahlnessNunattaQitornaiParty2020 for general information on Nunatta Qitornai and their policies.

All represented political parties are listed in @tbl-parties with additional information (where available) on their positions from the ParlGov dataset [@doringParlGov2022Release2022].

See @ackrenPoliticalPartiesGreenland2015 for an analysis of the development of Greenlandic political parties until 2014. For overviews of the Faroese political party system see @westSkipanarligarFortreytirOg2022 in Faroese and @westFaeroskPolitikMellem2020 in Danish.

```{r parties-list}
#| echo: false
#| message: false
#| label: tbl-parties
#| tbl-cap: List of political parties from Greenland and the Faroe Islands with a MP in Folketinget since 2004.

parties_gl <- subset(political_parties, Origin == "GL")[, !(names(political_parties) %in% "Origin")]
parties_fo <- subset(political_parties, Origin == "FO")[, !(names(political_parties) %in% "Origin")]

rownames(parties_gl) <- NULL
rownames(parties_fo) <- NULL

kable(parties_gl, caption = "Greenlandic Parties")
kable(parties_fo, caption = "Faroese Parties")
```

## Sample Plots

The following sample plots were generated from using `ggplot2` with the data available on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`. The plots show the distribution of votes cast by each MP that is part of the dataset. MPs are grouped by whether they are representing Greenland or the Faroe Islands. This overview makes no distinction between directly elected MPs and substitute MPs.

### Votes Per MP

```{r votes-per-mp}
#| echo: false
#| message: false
#| label: fig-votes-per-mp
#| fig-cap: Full voting records for each MP coded by the type of vote cast (for, against, absent, abstaining).

plot_votes <- ggplot(plot_dataset_ordered, aes(y = surname, fill = vote_type_id)) +
  geom_bar() +
  scale_x_continuous(expand = expansion(mult = c(0, .05))) +
  scale_y_discrete() +
  scale_fill_manual(
    name = "Vote",
    labels = c("for", "against", "absence", "abstention"),
    values = c("#6195CF", "#F7CB45", "#D1BBD7", "#777777")
  ) +

  facet_grid(origin ~ ., scales = "free_y", space = "free_y",
            labeller = labeller(origin = c("GL" = "Greenland", "FO" = "Faroe Islands"))
            ) +
    
  theme_nordatlantisk_basis()

plot_votes
```

### Votes Per MP Without Absences

```{r votes-per-mp-filtered}
#| echo: false
#| message: false
#| label: fig-votes-per-mp-filtered
#| fig-cap: Number of votes cast by each MP coded by the type of vote (for, against, abstaining). Only showing ballots when the MP is in attendance.

plot_dataset_without_absences_ordered <- plot_dataset_without_absences %>%
  mutate(surname = fct_reorder(surname, vote_type_id, .fun = length))

plot_votes_without_absences <- ggplot(plot_dataset_without_absences_ordered, aes(y = surname, fill = vote_type_id)) +
  geom_bar() +
  scale_x_continuous(expand = expansion(mult = c(0, .05))) +
  scale_y_discrete() +
  scale_fill_manual(
    name = "Vote",
    labels = c("for", "against", "abstention"),
    values = c("#6195CF", "#F7CB45", "#777777")
  ) +

  facet_grid(origin ~ ., scales = "free_y", space = "free_y",
          labeller = labeller(origin = c("GL" = "Greenland", "FO" = "Faroe Islands"))
          ) +

  theme_nordatlantisk_basis()

plot_votes_without_absences
```

### Votes Per MP Over Time

```{r votes-over-time}
#| echo: false
#| message: false
#| label: fig-votes-timeline
#| fig-cap: Distribution of votes over time per MP (for, against, absent, abstaining). Because there are so many data points, vertical jittering is added to make it a little easier to get an overview of the available data.

plot_dataset <- plot_dataset %>%
  mutate(surname = factor(surname, levels = levels(mandates$surname)))

scatterplot <- ggplot(plot_dataset %>%
                        arrange(desc(vote_type_id)),
                      aes(x = ballot_date, y = surname, color = vote_type_id)) +

  geom_jitter(width = 0, height = 0.2, size = 1.2, shape = 19, key_glyph = draw_key_rect) +
  scale_x_date(expand = expansion(mult = c(0.01, .05))) +
  scale_y_discrete() +
  
  scale_color_manual(
    name = "Vote",
    labels = c("for", "against", "absence", "abstention"),
    values = c("#6195CF", "#F7CB45", "#D1BBD7", "#777777")
  ) +

  guides(color = guide_legend(override.aes = list(fill = c("#6195CF", "#F7CB45", "#D1BBD7", "#777777")))) + 

  facet_grid(origin ~ ., scales = "free_y", space = "free_y",
        labeller = labeller(origin = c("GL" = "Greenland", "FO" = "Faroe Islands"))
        ) +

  theme_nordatlantisk_basis() +
  theme(axis.title.y = element_blank(),
        axis.line.y.left = element_blank(),
        panel.grid.major.y = element_line(color = "#777777", linewidth = 0.05))

scatterplot
```

### Votes Per MP Over Time Without Absences

```{r votes-over-time-filtered}
#| echo: false
#| message: false
#| label: fig-votes-timeline-filtered
#| fig-cap: Distribution of votes over time per MP (for, against, abstaining). Only showing ballots when the MP is in attendance. Because there are so many data points, vertical and horizontal jittering is added to make it a little easier to get an overview of the available data.

plot_dataset_without_absences <- plot_dataset_without_absences %>%
  mutate(surname = factor(surname, levels = levels(mandates$surname)))

scatterplot_without_absences <- ggplot(plot_dataset_without_absences %>% 
                                        arrange(vote_type_id),
                                      aes(x = ballot_date, y = surname, color = vote_type_id)) +

  geom_jitter(width = 0.4, height = 0.25, size = 1.2, shape = 19, alpha = 0.8, key_glyph = draw_key_rect) +
  scale_x_date(expand = expansion(mult = c(0.01, .05))) +
  scale_y_discrete(
  ) +
  
  scale_color_manual(
    name = "Vote",
    labels = c("for", "against", "abstention"),
    values = c("#6195CF", "#F7CB45", "#777777")
  ) +

  guides(color = guide_legend(override.aes = list(fill = c("#6195CF", "#F7CB45", "#777777"), alpha = 1))) + 

  facet_grid(origin ~ ., scales = "free_y", space = "free_y",
          labeller = labeller(origin = c("GL" = "Greenland", "FO" = "Faroe Islands"))
          ) +

  theme_nordatlantisk_basis() +
  theme(axis.title.y = element_blank(),
        axis.line.y.left = element_blank(),
        panel.grid.major.y = element_line(color = "#777777", linewidth = 0.05))

scatterplot_without_absences
```