---
title: A First Glance at nordatlantisk-ft
authors:
  - name: Moritz Twente
    affiliation: University of Basel
    email: moritz.twente@unibas.ch
    orcid: 0009-0005-7187-9774
date-modified: last-modified
bibliography: assets/nordatlantisk-ft.bib
link-citations: true
lang: en
---

```{r setup}
#| echo: false
#| message: false

# Setup -----
## Packages -----

library(here)
library(ggplot2)
library(dplyr)
library(readr)
library(knitr)

## Read Data -----

northatlantic_ft <- readRDS(here("data", "processed", "northatlantic_ft.rds"))

mp_names <- readRDS(here("data", "processed", "MP_names.rds"))

plot_dataset <- northatlantic_ft %>%
  left_join(mp_names %>% select(surname, origin), by = "surname")

political_parties <- read.csv(here("assets", "political-parties.csv"), sep = ";", check.names = FALSE)

## Manipulate Data -----

plot_dataset_without_absences <- subset(plot_dataset, vote_type_id != 3)
```

There are 179 MPs in Folketinget, the parliament of Denmark. But only 175 of them are elected in Denmark proper, while the remaining four seats are guaranteed for the so-called North Atlantic MPs from Greenland and the Faroe Islands, which both are autonomous members of the Danish Realm today after being under Danish colonial rule for centuries.

## Dataset

*nordatlantisk-ft* is compiled from data available on Folketingets Open Data platform [@folketingetFolketingetsAbneData2025] and comprises voting records of Northatlantic MPs. This includes records of `r length(unique(northatlantic_ft$ballot_id))` ballots in Folketinget as per the last update (`r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`). See the [Codebook](docs/codebook.qmd) for details and refer to @berntzenParliamentaryOpenData2019 for background information on Folketingets open data ecosystem.

## MPs

This dataset contains votes cast by Greenlandic and Faroese MPs since `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")`. There have been twenty individual politicians from Greenland or the Faroe Islands who served as MPs in the time frame covered by Folketinget's Open Data Platform. Twelve of them have been elected in Greenland and eight in the Faroe Islands.

```{r mp-list}
#| echo: false
#| message: false
#| label: tbl-MPs
#| tbl-cap: List of MPs from Greenland and the Faroe Islands in Folketinget since 2004.

MPs_gl <- subset(mp_names, origin == "GL")[, !(names(mp_names) %in% c("origin", "start_date", "end_date"))]
MPs_fo <- subset(mp_names, origin == "FO")[, !(names(mp_names) %in% c("origin", "start_date", "end_date"))]

rownames(MPs_gl) <- NULL
rownames(MPs_fo) <- NULL

kable(MPs_gl, caption = "MPs from Greenlandic Parties")
kable(MPs_fo, caption = "MPs from Faroese Parties")
```

## Political Parties

Since 2004, MPs from the Faroe Islands were members of four different political parties. Voters in Greenland elected politicians from two different political parties. However, a few of those switched party affiliation during their time as member of Folketinget and became members of newly formed parties (Nunatta Qitornai and Naleraq). All represented political parties are listed in @tbl-parties with additional information (where available) on their positions from the ParlGov dataset [@doringParlGov2022Release2022].

```{r parties-list}
#| echo: false
#| message: false
#| label: tbl-parties
#| tbl-cap: List of political parties from Greenland and the Faroe Islands with a MP in Folketinget since 2004.

parties_gl <- subset(political_parties, Origin == "GL")[, !(names(political_parties) %in% "Origin")]
parties_fo <- subset(political_parties, Origin == "FO")[, !(names(political_parties) %in% "Origin")]

rownames(parties_gl) <- NULL
rownames(parties_fo) <- NULL

kable(parties_gl, caption = "Greenlandic Parties")
kable(parties_fo, caption = "Faroese Parties")
```

## Sample Plots

The following sample plots were generated from using `ggplot2` with the data available on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`. The plots show the distribution of votes cast by each MP that is part of the dataset. MPs are grouped by whether they are representing Greenland or the Faroe Islands. This overview makes no distinction between directly elected MPs and substitute MPs.

### Votes Per MP

```{r votes-per-mp}
#| echo: false
#| message: false
#| label: fig-votes-per-mp
#| fig-cap: Full voting records for each MP coded by the type of vote cast (for, against, absent, abstaining).

plot_votes <- ggplot(plot_dataset, aes(y = surname, fill = vote_type_id)) +
  geom_bar() +
  scale_y_discrete() +
  scale_fill_manual(
    name = "Vote",
    labels = c("for", "against", "absence", "abstention"),
    values = c("#6195CF", "#F7CB45", "#D1BBD7", "#777777")
  ) +

  facet_grid(origin ~ ., scales = "free_y", space = "free_y",
            labeller = labeller(origin = c("GL" = "Greenland", "FO" = "Faroe Islands"))
            )

plot_votes
```

### Votes Per MP Without Absences

```{r votes-per-mp-filtered}
#| echo: false
#| message: false
#| label: fig-votes-per-mp-filtered
#| fig-cap: Voting records for each MP coded by the type of vote cast (for, against, abstaining). Only showing ballots when the MP is in attendance.

plot_votes_without_absences <- ggplot(plot_dataset_without_absences, aes(y = surname, fill = vote_type_id)) +
  geom_bar() +
  scale_y_discrete() +
  scale_fill_manual(
    name = "Vote",
    labels = c("for", "against", "abstention"),
    values = c("#6195CF", "#F7CB45", "#777777")
  ) +

  facet_grid(origin ~ ., scales = "free_y", space = "free_y",
          labeller = labeller(origin = c("GL" = "Greenland", "FO" = "Faroe Islands"))
          )

plot_votes_without_absences
```

### Votes Per MP Over Time

```{r votes-over-time}
#| echo: false
#| message: false

scatterplot <- ggplot(plot_dataset, aes(x = ballot_date, y = surname, color = vote_type_id)) +
  geom_point() +
  scale_y_discrete(
    ) +
  
  scale_color_manual(
    name = "Vote",
    labels = c("for", "against", "absence", "abstention"),
    values = c("#6195CF", "#F7CB45", "#D1BBD7", "#777777")
  ) +

  facet_grid(origin ~ ., scales = "free_y", space = "free_y",
        labeller = labeller(origin = c("GL" = "Greenland", "FO" = "Faroe Islands"))
        )

scatterplot
```

### Votes Per MP Over Time Without Absences

```{r votes-over-time-filtered}
#| echo: false
#| message: false

scatterplot_without_absences <- ggplot(plot_dataset_without_absences, aes(x = ballot_date, y = surname, color = vote_type_id)) +
  geom_point() +
  
  scale_y_discrete(
  ) +
  
  scale_color_manual(
    name = "Vote",
    labels = c("for", "against", "abstention"),
    values = c("#6195CF", "#F7CB45", "#777777")
  ) +
 #facet_wrap(~ origin, ncol = 1, scales = "free_y")
  facet_grid(origin ~ ., scales = "free_y", space = "free_y",
          labeller = labeller(origin = c("GL" = "Greenland", "FO" = "Faroe Islands"))
          )

scatterplot_without_absences
```