---
title: Codebook
authors:
  - name: Moritz Twente
    affiliation: University of Basel
    email: moritz.twente@unibas.ch
    orcid: 0009-0005-7187-9774
date-modified: last-modified
bibliography: ../assets/nordatlantisk-ft.bib
link-citations: true
lang: en
---

```{r setup}
#| echo: false
#| message: false

# Setup -----
## Packages -----

library(here)
library(ggplot2)
library(dplyr)
library(readr)
library(knitr)
library(forcats)
library(lubridate)

## Read Data -----

### List of MPs -----
mp_names <- readRDS(here("data", "processed", "MP_names.rds"))

### List of political parties -----
political_parties <- readRDS(here("data", "processed", "political_parties.rds"))

### Voting Records Database -----
northatlantic_votes <- readRDS(here("data", "processed", "northatlantic_votes.rds"))
northatlantic_votes_raw <- readRDS(here("data", "raw", "northatlantic_votes_raw.rds"))
ballot_info_raw <- readRDS(here("data", "raw", "ballot_info_raw.rds"))
ballot_results_ft <- readRDS(here("data", "processed", "ballot_results_ft.rds"))
ballot_topics_raw <- readRDS(here("data", "raw", "ballot_topics_raw.rds"))

northatlantic_ft <- readRDS(here("data", "processed", "northatlantic_ft.rds"))

plot_dataset <- northatlantic_ft %>%
  left_join(mp_names %>% select(MP_id, origin), by = "MP_id")

### Timeline of Mandates and Cabinets -----
mandates <- readRDS(here("data", "processed", "MP_dates.rds"))
election_dates <- readRDS(here("data", "processed", "election_dates.rds"))
cabinets_dk <- readRDS(here("data", "processed", "cabinets_dk.rds"))

cabinets_fo <- readRDS(here("data", "processed", "cabinets_fo.rds"))
cabinets_gl <- readRDS(here("data", "processed", "cabinets_gl.rds"))

#### Convert dates
mandates <- mandates %>%
  mutate(
    start = ymd(start),
    end   = ymd(end),
    # Replace NA in "end" with today's date
    end   = if_else(is.na(end), Sys.Date(), end)
  )

cabinets_fo <- cabinets_fo %>%
    mutate(
      start = ymd(start),
      end   = ymd(end),
      end   = coalesce(end, Sys.Date())
    )

cabinets_gl <- cabinets_gl %>%
    mutate(
      start = ymd(start),
      end   = ymd(end),
      end   = coalesce(end, Sys.Date())
    )

cabinets_dk <- cabinets_dk %>%
    mutate(
      start = ymd(start),
      end   = ymd(end),
      end   = coalesce(end, Sys.Date())
    )

cabinets_fo_gl <- full_join(cabinets_gl, cabinets_fo)

```

## Introduction {#introduction}

This codebook provides descriptions of the `nordatlantisk-ft` data set, i.e. of all files in `/data/`. Variables are described for each file individually with information on connections to other variables within the pipeline to create the data set. All data, unless otherwise specified, is retrieved from the records of the parliament of Denmark, @folketingetFolketingetsAbneData2025.

All data is available in `rds` format that can be read in an R Session via `readRDS()`. Where data is also available in `csv` format, the tabular metadata is provided in `json` files at `/data/processed/csv` according to the W3C Metadata Vocabulary for Tabular Data [@w3cW3CRecommendationMetadata2015].

## File and Variable Descriptions {#file-and-variable-descriptions}

The general structure of the data used in the workflow to compile the final `northatlantisk_ft.csv` output is illustrated in @fig-datamodel.

```{mermaid datamodel}
%%| label: fig-datamodel
%%| fig-cap: Chart illustrating the files used to create the dataset including variable names and types. Click on an element to jump to its description in the codebook.

classDiagram
    direction LR

    MP_dates .. MP_names
    MP_dates .. election_dates
    MP_dates .. political_parties

    MP_names *-- northatlantic_ft

    northatlantic_votes <|-- northatlantic_ft
    ballot_results_ft <|-- northatlantic_ft
    ballot_topics_raw <|-- northatlantic_ft

    MP_names *-- northatlantic_votes_raw
    northatlantic_votes_raw <|-- northatlantic_votes

    ballot_info_raw <|-- ballot_results_ft

    cabinets_fo .. cabinets_gl
    cabinets_gl .. cabinets_dk
    cabinets_dk <|-- northatlantic_ft

    MP_dates <|-- northatlantic_ft

    class northatlantic_ft {
        ballot_id : int
        MP_id : int
        surname : string
        origin: string
        party : string
        gvt_party_at_home: bool
        vote_type_id : int
        ballot_pass : bool
        ft_process_step : string
        ft_topic_id : int
        ft_topic : string
        ft_for : int
        ft_against : int
        ft_abstention : int
        ft_absent : int
        ballot_date : date
        ballot_type_id : int
        gvt_type_dk : string
        gvt_bloc_dk : string
        comment : string
        ballot_result_string : int
    }

        class northatlantic_votes {
        vote_id : int
        vote_type_id : int
        ballot_id : int
        MP_id : int
    }

        class MP_dates {
        period_id : string
        surname : string
        first_name : string
        MP_id: int
        origin: string
        party : string
        start : date
        end : date
        substitute : bool
    }

    class election_dates {
        election : string
        election_type : string
        date : date
    }

    class MP_names {
        surname : string
        first_name : string
        MP_id : int
        wikidata_id : string
        origin : string
        party : string
        substitute : bool
    }

    class ballot_results_ft {
        ballot_id : int
        meeting_id : int
        ballot_pass : bool
        ballot_date : date
        ft_for : int
        ft_against : int
        ft_abstention : int
        ft_absent : int
        ft_process_id : int
        ballot_nr : int
        ballot_type_id : int
        comment : string
        ballot_result_string : string
    }

    class ballot_info_raw {
        id : int
        nummer : int
        konklusion : string
        vedtaget : bool
        kommentar : string
        mødeid : int
        typeid : int
        sagstrinid : int
        opdateringsdato : date
    }

    class ballot_topics_raw {
        ft_process_id : int
        ft_process_step : string
        ft_topic_id : int
        ft_topic : string
    }

    class northatlantic_votes_raw {
        id : int
        typeid : int
        afstemningid : int
        aktørid : int
        opdateringsdato : date
    }

    class political_parties {
        party : string
        full_name : string
        wikidata_id : string
        party_family : string
        colour : string
        origin : string
        left_right : float
        state_market : float
        liberty_authority : float
        anti_pro_eu : float
    }

    class cabinets_fo {
      cabinet: string
      wikidata_id: string
      location: string
      start: date
      end: date
      FO_&ast;: bool
    }

    class cabinets_gl {
      cabinet: string
      wikidata_id: string
      location: string
      start: date
      end: date
      GL_&ast;: bool
    }

    class cabinets_dk {
      cabinet: string
      wikidata_id: string
      bloc: string
      type: string
      start: date
      end: date
      DK_&ast;: bool
    }

style ballot_info_raw fill:#D1BBD7
style ballot_results_ft fill:#D1BBD7

style ballot_topics_raw fill:#253C78,color:#FFFFFF

style northatlantic_ft fill:#F7CB45

style northatlantic_votes_raw fill:#FFEAAE
style northatlantic_votes fill:#FFEAAE

style MP_names fill:#6195CF,color:#FFFFFF
style MP_dates fill:#6195CF,color:#FFFFFF

click MP_dates href "#mp_dates" "tooltip"
click election_dates href "#election_dates" "tooltip"
click political_parties href "#political_parties" "tooltip"
click MP_names href "#mp_names" "tooltip"
click northatlantic_votes_raw href "#northatlantic_votes_raw" "tooltip"
click northatlantic_votes href "#northatlantic_votes" "tooltip"
click ballot_info_raw href "#ballot_info_raw" "tooltip"
click ballot_results_ft href "#ballot_results_ft" "tooltip"
click ballot_topics_raw href "#ballot_topics_raw" "tooltip"
click cabinets_fo href "#cabinets_fo" "tooltip"
click cabinets_gl href "#cabinets_gl" "tooltip"
click cabinets_dk href "#cabinets_dk" "tooltip"
click northatlantic_ft href "#northatlantic_ft" "tooltip"
```

### MP_names {#mp_names}

`MP_names` is provided in `csv` and `rds` formats in `/data/processed`.  Metadata for the `csv` file is provided in an accompanying `json` metadata file. This `csv` file serves as starting point for building the data set, as the workflow pipeline[^1] retrieves data from [Folketingets Open Data Portal](https://oda.ft.dk) based on which MPs are listed in this file. This repository is shipped with a list of all Folketinget MPs that have represented the Faroe Islands and Greenland from `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")` until the most recent update of this data set (on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`), which results in `r nrow(mp_names)` MPs.

[^1]: See [README](/index.qmd) or [`_targets.R`](/_targets.R)

```{r}
str(mp_names)
```

Descriptions of all variables in `MP_names` are provided in the following sections. The only variable necessary to execute the workflow is stored as [`MP_names$MP_id`](#mp_namesmp_id).

#### MP_names\$surname {#mp_namessurname}

All surname(s) are stored as values of the type `r typeof(mp_names$surname)`. Names are spelled according to standardised orthography and, in terms of morphology, in nominative (Faroese) resp. absolutive (Greenlandic) case. Because there are be multiple MPs with the same surname(s), refer to [`MP_names$MP_id`](#mp_namesmp_id) instead for reliable identification.

This column is not necessary for successfully executing the workflow pipeline, but it is used to map MP names to the corresponding IDs for increased readability of resulting plots.

```{r}
head(mp_names$surname)
```

#### MP_names\$first_name {#mp_namesfirst_name}

All first names are stored as values of the type `r typeof(mp_names$first_name)`. Names are spelled according to standardised orthography and, morphologically, in nominative (Faroese) resp. absolutive (Greenlandic) case. Because there may be multiple MPs with the same first name(s), refer to [`MP_names$MP_id`](#MP_names_MP_id) instead for reliable identification.

This column is not necessary for successfully executing the workflow pipeline, but it can be used to map MPs’ names to the corresponding IDs for increased readability of resulting plots.

```{r}
head(mp_names$first_name)
```

#### MP_names\$MP_id {#mp_namesmp_id}

Each MP is assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each `MP_id` thus is a unique identifier for one member of Folketinget. All IDs are stored as values of the type `r typeof(mp_names$MP_id)` as `r class(mp_names$MP_id)` variable. It is possible to use these IDs e.g. for querying the [the online database](https://oda.ft.dk) to retrieve documents that relate to a given MP or to find out which parliamentary processes this MP has been engaged in. The Folketing ID is also available as Wikidata Property [P10207](https://www.wikidata.org/wiki/Property:P10207).

`MP_id` is the only necessary column in `MP_names` for retrieving voting records. Most of the other variables are somehow used in post-processing, though.

```{r}
head(mp_names$MP_id)
```

This variable corresponds to the `aktørid` variable and the `Aktør` resource in [the Folketing online database](https://oda.ft.dk). Note that in Folketinget’s data model, ministries, parliamentary commissions, NGOs etc. are also listed as `Aktør` with their resp. `aktørid`.

#### MP_names\$wikidata_id {#mp_nameswikidata_id}

Apart from [`MP_names$MP_id`](#MP_names_MP_id), each MP's Wikidata QID is stored in `MP_names` for further processing options. This identifier can be used to query Wikidata to supplement the dataset with further information. At the moment, this identifier is not used in any step of the processing pipeline.

```{r}
head(mp_names$wikidata_id)
```

#### MP_names\$origin {#mp_namesorigin}

Using `ISO 3166-2` codes, `origin` indicates whether an MP was elected in either Greenland (`GL`) or the Faroe Islands (`FO`). This variable is stored as value of the type `r typeof(mp_names$origin)` as `r class(mp_names$origin)` variable. Note that this only indicates where the MP in question ran for office. MPs with ties to Greenland or the Faroe Islands who won a Folketinget mandate in a continental election district are thus not part of this data set, as they are not considered *Northatlantic* MPs.

```{r}
summary(mp_names$origin)
```

#### MP_names\$party {#mp_namesparty}

The political party that each MP belongs to is stored as value of the type `r typeof(mp_names$party)` as `r class(mp_names$party)` variable.

Since 2004, MPs from the Faroe Islands were members of `r sum(political_parties$origin == "FO")` different political parties. Voters in Greenland elected politicians from `r sum(political_parties$origin == "GL") - 2` different political parties. However, as per `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %Y")`, there have been two MPs from Greenland who left their party – Siumut, in both cases – during their time in office and joined other parties (Nunatta Qitornai and Naleraq[^2]).

[^2]: Both parties have been formed quite recently. See @ahlnessNunattaQitornaiParty2020 for general information on Nunatta Qitornai and their policies. Nunatta Qitornai has de facto been dissolved after the 2021 Inatsisartut election [@hviidVittusQujaukitsoqMelder2025].

For now, the `MP_names` data frame does not include information on membership periods etc. At the moment, these two cases are therefore stored with a single string without distinguishing between membership periods. Instead, a timeline of party membership(s) can be inferred using the information available in [`MP_dates`](#mp_dates). See also [`political_parties`](#political_parties).

```{r}
summary(mp_names$party)
```

All represented political parties are listed in @tbl-parties with additional information (where available) on their positions from the ParlGov dataset [@doringParlGov2022Release2022].

```{r parties-list}
#| echo: false
#| message: false
#| label: tbl-parties
#| tbl-cap: List of political parties from Greenland and the Faroe Islands with a MP in Folketinget since 2004.

political_parties_printable <- political_parties |>
  mutate(
    full_name_linked = ifelse(
      is.na(wikidata_id) | wikidata_id == "",
      full_name,
      paste0("[", full_name, "](https://wikidata.org/wiki/", wikidata_id, ")")
    )
  )

parties_gl_printable <- political_parties_printable |>
  filter(origin == "GL") |>
  select(party, full_name_linked, party_family,
         left_right, state_market, liberty_authority, anti_pro_eu)

parties_fo_printable <- political_parties_printable |>
  filter(origin == "FO") |>
  select(party, full_name_linked, party_family,
         left_right, state_market, liberty_authority, anti_pro_eu)

printable_names <- c(
  "Party", "Full Name", "Party Family",
  "Left–Right", "State–Market", "Liberty–Authority", "Anti–Pro-EU"
)

kable(
  parties_gl_printable,
  caption = "Greenlandic Parties",
  col.names = printable_names,
  row.names = FALSE,
  escape = FALSE
)

kable(
  parties_fo_printable,
  caption = "Faroese Parties",
  col.names = printable_names,
  row.names = FALSE,
  escape = FALSE)
```

#### MP_names\$substitute {#mp_namessubstitute}

Some of the politicians that are part of this data set joined Folketinget in the role of a substitute member, filling in for the originally elected MPs while they were on leave [cf. @harderFaeroskeOgGronlandske2022, 12-13]. Doris Jakobsen (SIU), Lisbeth Petersen (B), Magni Arge (E) and Sjúrður Skaale (C) all first became MPs as substitute members, but later joined as regular MPs after a general election. For now, they are listed as full members in `MP_names`. More detailed data on membership periods is available in [`MP_dates`](#mp_dates).

```{r}
summary(mp_names$substitute)
```

------------------------------------------------------------------------

### MP_dates {#mp_dates}

`MP_dates` is provided in `csv` and `rds` formats in `/data/processed`.  Metadata for the `csv` file is provided in an accompanying `json` metadata file. The dataset includes detailed information on membership timelines of MPs in Folketinget. Because a substantial share of MPs from Greenland and the Faroe Islands were absent for a longer period [@harderFaeroskeOgGronlandske2022, 12-13], there have been a number of substitute MPs (stedfortræder) replacing the originally elected politicians during their time(s) of absence. Those MPs are listed here as well. As of `r format(file.info(here("data", "processed", "csv", "MP_dates.csv"))$mtime, "%B %d, %Y")`, `MP_dates` includes `r nrow(mandates)` observations of `r ncol(mandates)` variables.

```{r}
str(mandates)
```

Descriptions of all variables in `MP_dates` are provided in the following sections.

#### MP_dates\$period_id {#mp_datesperiod_id}

Each recorded membership period can be reliably identified by using the `period_id` variable, allowing to distinguish between multiple membership periods of the same politician(s). Period IDs are stored as `r class(mandates$period_id)` variables.

```{r}
head(mandates$period_id)
```

#### MP_dates\$surname {#mp_datessurname}

All surname(s) are stored as values of the type `r typeof(mandates$surname)`. Names are spelled according to standardised orthography and, in terms of morphology, in nominative (Faroese) resp. absolutive (Greenlandic) case. Because there are be multiple MPs with the same surname(s), refer to [`MP_dates$MP_id`](#mp_datesmpid) instead for reliable identification of each MP and to [`MP_dates$period_id`](#mp_datesperiod_id) for reliable identification of membership periods. See also [`MP_names$surname`](#mp_namessurname).

```{r}
str(mandates$surname)
```

#### MP_dates\$first_name {#mp_datesfirst_name}

All first names are stored as values of the type `r typeof(mandates$first_name)`. Names are spelled according to standardised orthography and, morphologically, in nominative (Faroese) resp. absolutive (Greenlandic) case. Because there may be multiple MPs with the same first name(s), refer to [`MP_dates$MP_id`](#mp_datesmpid) instead for reliable identification. See also [`MP_names$first_name`](#mp_namesfirst_name).

```{r}
str(mandates$first_name)
```

#### MP_dates\$MP_id {#mp_datesmpid}

Each MP is assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each `MP_id` thus is a unique identifier for one member of Folketinget. All IDs are stored as values of the type `r typeof(mandates$MP_id)` as `r class(mandates$MP_id)` variable. It is possible to use these IDs e.g. for querying the [the online database](https://oda.ft.dk) to retrieve documents that relate to a given MP or to find out which parliamentary processes this MP has been engaged in. The Folketing ID is also available as Wikidata Property [P10207](https://www.wikidata.org/wiki/Property:P10207). See also [`MP_names$mP_id`](#mp_namesmp_id).

```{r}
str(mandates$MP_id)
```

#### MP_dates\$origin {#mp_datesorigin}

Using `ISO 3166-2` codes, `origin` indicates whether an MP was elected in either Greenland (`GL`) or the Faroe Islands (`FO`). This variable is stored as value of the type `r typeof(mandates$origin)` as `r class(mandates$origin)` variable. Note that this only indicates where the MP in question ran for office. MPs with ties to Greenland or the Faroe Islands who won a Folketinget mandate in a continental election district are thus not part of this data set, as they are not considered *Northatlantic* MPs.

```{r}
table(mandates$origin)
```

#### MP_dates\$party {#mp_datesparty}

The political party that each MP belongs to is stored as value of the type `r typeof(mandates$party)` as `r class(mandates$party)` variable. See [`MP_names$party`](#mp_namesparty) and [`political_parties`](#political_parties) for more information. In contrast to those, `MP_dates$party` actually provides information on changing party membership(s) since membership entries are split up on a timeline. This way, it's possible to match each recorded vote to the valid party membership at a specific point in time.

Note that the value `UF` means that the MP is not a member of a political group/party at the time ("uden for folketingsgrupperne").

```{r}
unique(mandates$party)
```

#### MP_dates\$start {#mp_datesstart}

The date on which each membership period begins is stored as `r class(mandates$start)` variable of the type `r typeof(mandates$start)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(mandates$start), "%B %d, %Y")` (`r min(mandates$start)`) and the most recent entry from `r format(max(mandates$start), "%B %d, %Y")` (`r max(mandates$start)`) as of `r format(file.info(here("data", "processed", "csv", "MP_dates.csv"))$mtime, "%B %Y")`.

In this data set, a membership period is either starting when a politicians joins Folketinget for the first time, if the MP in question is re-joining after being replaced by a temporary substitute member or if there is a change in party affiliation.

```{r}
head(mandates$start)
```

#### MP_dates\$end {#mp_datesend}

The date on which each membership period ends is stored as `r class(mandates$end)` variable of the type `r typeof(mandates$end)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(mandates$end), "%B %d, %Y")` (`r min(mandates$end)`) as of `r format(file.info(here("data", "processed", "csv", "MP_dates.csv"))$mtime, "%B %Y")`.

In this data set, a membership period ends either when a politicians leaves Folketinget for good, if the MP in question is temporarily being replaced by a temporary substitute member or if there is a change in party affiliation.

```{r}
head(mandates$end)
```

#### MP_dates\$substitute {#mp_datessubstitute}

Some of the politicians that are part of this data set joined Folketinget in the role of a substitute member, filling in for the originally elected MPs while they were on leave [cf. @harderFaeroskeOgGronlandske2022, 12-13]. Doris Jakobsen (SIU), Lisbeth Petersen (B), Magni Arge (E) and Sjúrður Skaale (C) all first became MPs as substitute members, but later joined as regular MPs after a general election. In contrast to the data in [`MP_names$substitute`](#mp_namessubstitute), the data available in `MP_dates$substitute` also distinguishes between MPs that first joined as substitute MPs but became regular MPs at a later date.

As per `r format(file.info(here("data", "processed", "csv", "MP_dates.csv"))$mtime, "%B %d, %Y")`, `r length(unique(mandates$MP_id[mandates$substitute]))` substitute MPs have joined Folketinget in total.

`r sum(mp_names$substitute == TRUE)` of the politicians that are part of this data set joined Folketinget in the role of a substitute member[^3], filling in for one of the `r sum(mp_names$substitute == FALSE)` originally elected MPs while they were on leave [cf. @harderFaeroskeOgGronlandske2022, 12-13].

[^3]: See [README](/index.qmd) or [`_targets.R`](/_targets.R)

```{r}
table(mandates$substitute)
```

------------------------------------------------------------------------

### election_dates {#election_dates}

This repository is shipped with a list of all elections to the parliaments in Denmark (Folketinget), Greenland (Inatsisartut) and the Faroe Islands (Løgtingið) that led to the formation of the parliaments in session during the time period covered by this data set. This translates to `r nrow(election_dates[election_dates$election_type == "Folketing Election",])` elections to Folketing, `r nrow(election_dates[election_dates$election_type == "Inatsisartut Election",])` elections to Inatsisartut, and `r nrow(election_dates[election_dates$election_type == "Løgting Election",])` elections to Løgting. The earliest election included is the one held on `r format(min(election_dates$date), "%B %d, %Y")`, while the most recent election included was held on `r format(max(election_dates$date), "%B %d, %Y")`.

The contents of `election_dates` is not used during the workflow to compile the final `northatlantik_ft` data set, but is used as secondary data for visualisation purposes.

`election_dates` is provided in `csv` and `rds` formats in `/data/processed`. Metadata for the `csv` file is provided in an accompanying `json` metadata file. These files are compiled by executing the script at [`src/create_election_list.R`](/src/create_election_list.R) and following elections should be added by updating this script.

```{r}
str(election_dates)
```

Descriptions of all variables in `election_dates` are provided in the following sections.

#### election_dates\$election

Each recorded election can be reliably identified by using the `election` variable. All entries are stored as values of the type `r typeof(election_dates$election)` as `r class(election_dates$election)` variable.

```{r}
head(election_dates$election)
```

#### election_dates\$election_type

The `election_dates` dataset includes elections to three different parliaments: Danish Folketinget, Greenlandic Inatsisartut and Faroese Løgtingið. To distinguish between elections, the type of election is stored in `election_dates$election_type`. All entries are stored as values of the type `r typeof(election_dates$election_type)` as `r class(election_dates$election_type)` variable.

```{r}
table(election_dates$election_type)
```

#### election_dates\$date

The date of each election is stored in `election_dates$date`, indicating the day of voting. All entries are stored as values of the type `r typeof(election_dates$date)` as `r class(election_dates$date)` variable. The dates are formatted using the `%Y-%m-%d` notation.

Note that the 2022 Folketing election which took place in Denmark and Greenland on `r format(as.Date("2022-11-01"), "%B %d, %Y")` was held earlier on the Faroe Islands -- it was moved up to `r format(as.Date("2022-10-31"), "%B %d, %Y")` due to a Faroese public holiday [@statsministerietValgdatoPaFaeroerne2022].

```{r}
str(election_dates$date)
```

------------------------------------------------------------------------

### political_parties {#political_parties}

This repository is shipped with a list of political parties that have been represented in Folketinget during the time period covered by this data set. This list was most recently updated on `r format(file.info(here("data", "processed", "csv", "political_parties.csv"))$mtime, "%B %d, %Y")` and includes `r nrow(political_parties)` political parties. From these parties, `r nrow(political_parties[political_parties$origin == "GL", ])` are from Greenland and `r nrow(political_parties[political_parties$origin == "FO", ])` from the Faroe Islands.

The contents of `election_dates` is not used during the workflow to compile the final `northatlantik_ft` data set, but is used as secondary data for visualisation purposes.

`political_parties` is provided is provided in `csv` and `rds` formats in `/data/processed`. Metadata for the `csv` file is provided in an accompanying `json` metadata file. See also [`MP_names$party`](#mp_namesparty).

```{r}
str(political_parties)
```

Descriptions of all variables in `political_parties` are provided in the following sections.

#### political_parties\$party

The `party` variable of `political_parties` stores the common abbreviation for each party. All entries are stored as values of the type `r typeof(political_parties$party)` as `r class(political_parties$party)` variable.

Note that while political parties in Greenland are abbreviated using letters actually corresponding to their official names, this is not the case for parties in Denmark and and the Faroe Islands. Here, parties are often referred to by their one-letter reference code ([*Bogstavsbetegnelser*](https://www.valg.im.dk/partier-og-kandidater/partiernes-bogstavbetegnelser)). This code does not necessarily correspond to any part of the party's official name, but is simply a commonly used shorthand for the party. For example, the Faroese Social Democratic Party (Javnaðarflokkurin) is commonly labelled as `C`, even though the letter does not appear anywhere in the party's name.

```{r}
str(political_parties$party)
```

#### political_parties\$full_name

The `full_name` variable of `political_parties` stores the full name for each party. All entries are stored as values of the type `r typeof(political_parties$full_name)` as `r class(political_parties$full_name)` variable.

```{r}
str(political_parties$full_name)
```

#### political_parties\$wikidata_id {#political_partieswikidata_id}

The `wikidata_id` variable stores the `QID` linking to the Wikidata entity representing the political party in question, making it easy to retrieve additional information from Wikidata, if necessary. This variable is stored as value of the type `r typeof(political_parties$wikidata_id)` as `r class(political_parties$wikidata_id)` variable.

```{r}
head(political_parties$wikidata_id)
```

#### political_parties\$party_family

The `party_family` variable of `political_parties` stores the label for the political party family the party is matched with in the ParlGov dataset [@doringParlGov2022Release2022]. All entries are stored as values of the type `r typeof(political_parties$party_family)` as `r class(political_parties$party_family)` variable.

Note that party families are not listed for parties that have MPs in Folketinget for the first time after the last update of the ParlGov dataset (`r paste(political_parties$full_name[is.na(political_parties$party_family) | political_parties$party_family == ""], collapse = ", ")`).

```{r}
head(political_parties$party_family)
```

#### political_parties\$colour

The `colour` variable of `political_parties` stores `HEX` codes corresponding to the colour usually associated with the party. All entries are stored as values of the type `r typeof(political_parties$colour)` as `r class(political_parties$colour)` variable. The codes are retrieved from each party's Wikipedia article.

```{r}
head(political_parties$colour)
```

#### political_parties\$origin

Using `ISO 3166-2` codes, `origin` indicates whether a party stands for election in either Greenland (`GL`) or the Faroe Islands (`FO`). This variable is stored as value of the type `r typeof(political_parties$origin)` as `r class(political_parties$origin)` variable. As per `r format(file.info(here("data", "processed", "csv", "political_parties.csv"))$mtime, "%B %Y")`, `political_parties` lists `r nrow(political_parties[political_parties$origin == "GL", ])` Greenlandic and `r nrow(political_parties[political_parties$origin == "FO", ])` Faroese parties.

```{r}
table(political_parties$origin)
```

#### political_parties\$left_right

`left_right` indicates where a party's positions are located on a scale from 0 (left) to 10 (right). Values are taken directly from the ParlGov dataset [@doringParlGov2022Release2022]. This variable is stored as value of the type `r typeof(political_parties$left_right)` as `r class(political_parties$left_right)` variable.

Note that party positions are not listed for parties that have MPs in Folketinget for the first time after the last update of the ParlGov dataset (`r paste(political_parties$full_name[is.na(political_parties$left_right) | political_parties$left_right == ""], collapse = ", ")`).

```{r}
head(political_parties$left_right)
```

#### political_parties\$state_market

`state_market` indicates where a party's positions on regulating the economy are located on a scale from 0 (preferring state regulations) to 10 (preferring unregulated markets). Values are taken directly from the ParlGov dataset [@doringParlGov2022Release2022]. This variable is stored as value of the type `r typeof(political_parties$state_market)` as `r class(political_parties$state_market)` variable.

Note that party positions are not listed for parties that have MPs in Folketinget for the first time after the last update of the ParlGov dataset (`r paste(political_parties$full_name[is.na(political_parties$left_right) | political_parties$left_right == ""], collapse = ", ")`).

```{r}
head(political_parties$state_market)
```

#### political_parties\$liberty_authority

`liberty_authority` indicates a party's position on a scale from 0 (libertarian) to 10 (authoritarian). Values are taken directly from the ParlGov dataset [@doringParlGov2022Release2022]. This variable is stored as value of the type `r typeof(political_parties$liberty_authority)` as `r class(political_parties$liberty_authority)` variable.

Note that party positions are not listed for parties that have MPs in Folketinget for the first time after the last update of the ParlGov dataset (`r paste(political_parties$full_name[is.na(political_parties$left_right) | political_parties$left_right == ""], collapse = ", ")`).

```{r}
head(political_parties$liberty_authority)
```

#### political_parties\$anti_pro_eu

`anti_pro_eu` indicates a party's position towards EU integration on a scale from 0 (in favor of EU integration) to 10 (against EU integration). Values are taken directly from the ParlGov dataset [@doringParlGov2022Release2022]. This variable is stored as value of the type `r typeof(political_parties$anti_pro_eu)` as `r class(political_parties$anti_pro_eu)` variable.

Note that party positions are not listed for parties that have MPs in Folketinget for the first time after the last update of the ParlGov dataset (`r paste(political_parties$full_name[is.na(political_parties$left_right) | political_parties$left_right == ""], collapse = ", ")`).

```{r}
head(political_parties$anti_pro_eu)
```

------------------------------------------------------------------------

### northatlantic_votes {#northatlantic_votes}

`northatlantic_votes` is provided as `rds` file in `/data/processed/`. After all votes cast by the MPs specified in [`MP_names`](#mp_names) are downloaded, they are processed and then stored in this file. The unprocessed [raw data](#northatlantic_votes_raw) is available as `csv` file in `/data/raw/`. As per `r format(file.info(here("data", "processed", "northatlantic_votes.rds"))$mtime, "%B %Y")`, `northatlantic_votes.rds` contains `r nrow(northatlantic_votes)` observations of `r ncol(northatlantic_votes)` variables.

```{r}
str(northatlantic_votes)
```

Descriptions of all variables in `northatlantic_votes` are provided in the following sections.

#### northatlantic_votes\$vote_id {#northatlantic_votesvote_id}

All votes cast in Folketinget are assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each vote ID is thus a unique identifier for one vote cast in Folketinget. All IDs are stored as values of the type `r typeof(northatlantic_votes$vote_id)` as `r class(northatlantic_votes$vote_id)` variable.

This variable corresponds to the `id` variable and the `Stemme` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
head(northatlantic_votes$vote_id)
```

#### northatlantic_votes\$vote_type_id {#northatlantic_votesvote_type_id}

All votes cast in Folketinget are recorded using numeric values that correspond to the MP’s decision (see @tbl-typeid). All Vote Type IDs are stored as values of the type `r typeof(northatlantic_votes$vote_type_id)` as `r class(northatlantic_votes$vote_type_id)` variable.

| ID | Result | English | n |
|:-----------------|:------------------|:-----------------|-----------------:|
| 1 | for | for | `r length(northatlantic_votes$vote_type_id[northatlantic_votes$vote_type_id == "1"])` |
| 2 | imod | against | `r length(northatlantic_votes$vote_type_id[northatlantic_votes$vote_type_id == "2"])` |
| 3 | fravær | absence | `r length(northatlantic_votes$vote_type_id[northatlantic_votes$vote_type_id == "3"])` |
| 4 | hverken for eller imod | abstention | `r length(northatlantic_votes$vote_type_id[northatlantic_votes$vote_type_id == "4"])` |

: Vote Type IDs as used by Folketingets Open Data Service {#tbl-typeid} {.striped .hover}

This variable corresponds to the `typeid` variable and the `Stemmetype` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
head(northatlantic_votes$vote_type_id)
```

#### northatlantic_votes\$ballot_id {#northatlantic_votesballot_id}

All ballot procedures in Folketinget are assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each ballot ID is thus a unique identifier for one ballot in Folketinget. All IDs are stored as values of the type `r typeof(northatlantic_votes$ballot_id)` as `r class(northatlantic_votes$ballot_id)` variable.

This variable corresponds to the [`ballot_results_ft$ballot_id`](#ballot_results_ftballot_id) variable and the `Afstemning` resource in [the Folketing online database](https://oda.ft.dk). Take care not to confuse `ballot_id` with [`ballot_results_ft$ballot_nr`](#ballot_results_ftballot_nr).

```{r}
head(northatlantic_votes$ballot_id)
```

#### northatlantic_votes\$MP_id {#northatlantic_votesmp_id}

See [`MP_names$MP_id`](#mp_namesmp_id).

```{r}
head(northatlantic_votes$MP_id)
```

------------------------------------------------------------------------

### northatlantic_votes_raw {#northatlantic_votes_raw}

`northatlantic_votes_raw` is provided as `rds` file in `/data/raw/`. It contains the downloaded data on voting records before any preprocessing. The [processed data](#northatlantic_votes) is available as `rds` file in `/data/processed`. As of `r format(file.info(here("data", "raw", "northatlantic_votes_raw.rds"))$mtime, "%B %Y")`, `northatlantic_votes_raw.rds` contains `r nrow(northatlantic_votes_raw)` observations of `r ncol(northatlantic_votes_raw)` variables.

```{r}
str(northatlantic_votes_raw)
```

Descriptions of all variables in `northatlantic_votes_raw` are provided in the following sections.

#### northatlantic_votes_raw\$id

See [`northatlantic_votes$vote_id`](#northatlantic_votesvote_id). In the raw data, `id` is stored as `r typeof(northatlantic_votes_raw$id)` value.

```{r}
head(northatlantic_votes_raw$id)
```

#### northatlantic_votes_raw\$typeid

See [`northatlantic_votes$vote_type_id`](#northatlantic_votesvote_type_id). In the raw data, `typeid` is stored as `r typeof(northatlantic_votes_raw$typeid)` value.

```{r}
table(northatlantic_votes_raw$typeid)
```

#### northatlantic_votes_raw\$afstemningid

See [`northatlantic_votes$ballot_id`](#northatlantic_votesballot_id). In the raw data, `afstemningid` is stored as `r typeof(northatlantic_votes_raw$afstemningid)` value.

Take care not to confuse `afstemningid` with [`ballot_results_ft$ballot_nr`](#ballot_results_ftballot_nr).

```{r}
head(northatlantic_votes_raw$afstemningid)
```

#### northatlantic_votes_raw\$aktørid

See [`northatlantic_votes$MP_id`](#northatlantic_votesmp_id). In the raw data, `aktørid` is stored as `r typeof(northatlantic_votes_raw$aktørid)` value.

```{r}
head(northatlantic_votes_raw$aktørid)
```

#### northatlantic_votes_raw\$opdateringsdato

For all records kept in [the Folketing online database](https://oda.ft.dk), the time stamp of its most recent update is stored in `opdateringsdato`. All dates are stored as values of the type `r typeof(northatlantic_votes_raw$opdateringsdato)`. The time stamps are originally formatted as `%Y-%m-%dT%T`, with some values even at split second level, but simplified to `%Y-%m-%d` after downloading.

This variable is eliminated from [`northatlantic_votes`](#northatlantic_votes) as a result of data processing.

```{r}
head(northatlantic_votes_raw$opdateringsdato)
```

------------------------------------------------------------------------

### ballot_results_ft {#ballot_results_ft}

`ballot_results_ft` is provided as `rds` file in `/data/processed/`. After all ballots are downloaded, they are processed and then stored in this file. The unprocessed [raw data](#ballot_info_raw) is available as `rds` file in `/data/raw/`. As of `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`, `ballot_results_ft.rds` contains `r nrow(ballot_results_ft)` observations of `r ncol(ballot_results_ft)` variables.

```{r}
str(ballot_results_ft)
```

Descriptions of all variables in `ballot_results_ft` are provided in the following sections.

#### ballot_results_ft\$ballot_id {#ballot_results_ftballot_id}

See [northatlantic_votes\$ballot_id](#northatlantic_votesballot_id). Take care not to confuse `ballot_id` with [`ballot_nr`](#ballot_results_ftballot_nr).

```{r}
head(ballot_results_ft$ballot_id)
```

#### ballot_results_ft\$meeting_id {#ballot_results_ftmeeting_id}

All meetings in Folketinget are assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each meeting ID is thus a unique identifier for one meeting in Folketinget. All IDs are stored as values of the type `r typeof(ballot_results_ft$meeting_id)` as `r class(ballot_results_ft$meeting_id)` variable.

This variable corresponds to the [`mødeid`](#ballot_info_rawmødeid) variable and the `Møde` resource in [the Folketing online database](https://oda.ft.dk).

This variable is eliminated when joining `ballot_results_ft` and `northatlantic_votes` to [`northatlantic_ft`](#northatlantic_ft).

```{r}
head(ballot_results_ft$meeting_id)
```

#### ballot_results_ft\$ballot_pass {#ballot_results_ftballot_pass}

The result of all ballots in Folketinget is stored in `ballot_pass` as `r typeof(ballot_results_ft$ballot_pass)` variable. If parliament votes in favor of a proposal, it passes and `ballot_pass` is assigned `TRUE`; if parliament votes a proposal down, it does not pass and `ballot_pass` is assigned `FALSE`.

This variable corresponds to the [`vedtaget`](#ballot_info_rawvedtaget) variable in the `Afstemning` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
summary(ballot_results_ft$ballot_pass)
```

#### ballot_results_ft\$ballot_date {#ballot_results_ftballot_date}

The date on which each ballot takes place in Folketinget is stored as `r class(ballot_results_ft$ballot_date)` variable of the type `r typeof(ballot_results_ft$ballot_date)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(ballot_results_ft$ballot_date), "%B %d, %Y")` (`r min(ballot_results_ft$ballot_date)`) and the most recent entry from `r format(max(ballot_results_ft$ballot_date), "%B %d, %Y")` (`r max(ballot_results_ft$ballot_date)`) as of `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`.

This variable is added to the data using the [`get_meeting_dates()`](/src/targets/get_meeting_dates.R) function.

```{r}
head(ballot_results_ft$ballot_date)
```

#### ballot_results_ft\$ft_for {#ballot_results_ftft_for}

In `ft_for`, the number of votes cast in favor of a proposal is stored as `r class(ballot_results_ft$ft_for)` variable of the type `r typeof(ballot_results_ft$ft_for)`.

The open records kept by Folketinget are inconsistent regarding the coding of ballot results: Overall results are stored in a single [`ballot_result_string`](#ballot_results_ftballot_result_string) in Danish, listing votes in favor as well as votes against and abstentions in the same string. However, for some records, there are no result strings listing the vote counts (technically, there are empty strings). For these records, records have to be pulled from the API individually. This concerns `r sum(is.na(ballot_results_ft$ballot_result_string))` out of `r nrow(ballot_results_ft)` observations as of `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`. Affected are mostly votes from dates earlier than June 2010, when Folketinget appears to have switched their way of record keeping to the current setup with results given as a string.

In [`get_missing_ballot_counts.R`](/src/targets/get_missing_ballot_counts.R), the overall count of votes in favor of the proposal are first extracted from [`ballot_result_string`](#ballot_results_ftballot_result_string) (where available) using [`str_nth_number()`](https://rorynolan.github.io/strex/reference/str_nth_number.html) from the strex package [@nolanStrexExtraString2024]. Even though the wording used in the ballot result string also differs over time, I rely on the order of the results being presented to extract the votes in favor of the proposal at hand. In a second step, I filter those cases in `ballot_results_ft` where there is an empty string in `ballot_result_string` (`r sum(is.na(ballot_results_ft$ballot_result_string))` out of `r nrow(ballot_results_ft)`). For those observations, I retrieve the number of votes in favor from the Folketinget ODA API. This information is then merged back into the `ballot_results_ft` data frame.

The maximum value stored in `ft_for` is `r max(ballot_results_ft$ft_for, na.rm = TRUE)` and the minimum value stored in `ft_for` is `r min(ballot_results_ft$ft_for, na.rm = TRUE)`. As the total number of MPs in Folketinget is 179, the value of `ft_for` cannot be greater than `179`.

```{r}
summary(ballot_results_ft$ft_for)
```

#### ballot_results_ft\$ft_against {#ballot_results_ftft_against}

In `ft_against`, the number of votes cast in favor of a proposal is stored as `r class(ballot_results_ft$ft_against)` variable of the type `r typeof(ballot_results_ft$ft_against)`.

The open records kept by Folketinget are inconsistent regarding the coding of ballot results: Overall results are stored in a single [`ballot_result_string`](#ballot_results_ftballot_result_string) in Danish, listing votes against as well as votes in favor and abstentions in the same string. However, for some records, there are no result strings listing the vote counts (technically, there are empty strings). For these records, records have to be pulled from the API individually. This concerns `r sum(is.na(ballot_results_ft$ballot_result_string))` out of `r nrow(ballot_results_ft)` observations as of `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`. Affected are mostly votes from dates earlier than June 2010, when Folketinget appears to have switched their way of record keeping to the current setup with results given as a string.

In [`get_missing_ballot_counts.R`](/src/targets/get_missing_ballot_counts.R), the overall count of votes against of the proposal are first extracted from [`ballot_result_string`](#ballot_results_ftballot_result_string) (where available) using [`str_nth_number()`](https://rorynolan.github.io/strex/reference/str_nth_number.html) from the strex package [@nolanStrexExtraString2024]. Even though the wording used in the ballot result string also differs over time, I rely on the order of the results being presented to extract the votes against the proposal at hand. In a second step, I filter those cases in `ballot_results_ft` where there is an empty string in `ballot_result_string` (`r sum(is.na(ballot_results_ft$ballot_result_string))` out of `r nrow(ballot_results_ft)`). For those observations, I retrieve the number of votes against from the Folketinget ODA API. This information is then merged back into the `ballot_results_ft` data frame.

The maximum value stored in `ft_against` is `r max(ballot_results_ft$ft_against, na.rm = TRUE)` and the minimum value stored in `ft_against` is `r min(ballot_results_ft$ft_against, na.rm = TRUE)`. As the total number of MPs in Folketinget is 179, the value of `ft_against` cannot be greater than `179`.

```{r}
summary(ballot_results_ft$ft_against)
```

#### ballot_results_ft\$ft_abstention {#ballot_results_ftft_abstention}

In `ft_abstention`, the number of abstentions in a vote is stored as `r class(ballot_results_ft$ft_abstention)` variable of the type `r typeof(ballot_results_ft$ft_abstention)`.

The open records kept by Folketinget are inconsistent regarding the coding of ballot results: Overall results are stored in a single [`ballot_result_string`](#ballot_results_ftballot_result_string) in Danish, listing abstentions against as well as votes in favor and against in the same string. However, for some records, there are no result strings listing the vote counts (technically, there are empty strings). For these records, records have to be pulled from the API individually. This concerns `r sum(is.na(ballot_results_ft$ballot_result_string))` out of `r nrow(ballot_results_ft)` observations as of `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`. Affected are mostly votes from dates earlier than June 2010, when Folketinget appears to have switched their way of record keeping to the current setup with results given as a string.

In [`get_missing_ballot_counts.R`](/src/targets/get_missing_ballot_counts.R), the overall count of abstaining votes on the proposal are first extracted from [`ballot_result_string`](#ballot_results_ftballot_result_string) (where available) using [`str_nth_number()`](https://rorynolan.github.io/strex/reference/str_nth_number.html) from the strex package [@nolanStrexExtraString2024]. Even though the wording used in the ballot result string also differs over time, I rely on the order of the results being presented to extract the number of abstentions. In a second step, I filter those cases in `ballot_results_ft` where there is an empty string in `ballot_result_string` (`r sum(is.na(ballot_results_ft$ballot_result_string))` out of `r nrow(ballot_results_ft)`). For those observations, I retrieve the number of abstentions from the Folketinget ODA API. This information is then merged back into the `ballot_results_ft` data frame.

The maximum value stored in `ft_abstention` is `r max(ballot_results_ft$ft_abstention, na.rm = TRUE)` and the minimum value stored in `ft_abstention` is `r min(ballot_results_ft$ft_abstention, na.rm = TRUE)`. As the total number of MPs in Folketinget is 179, the value of `ft_abstention` cannot be greater than `179`.

```{r}
summary(ballot_results_ft$ft_abstention)
```

#### ballot_results_ft\$ft_absent {#ballot_results_ftft_absent}

In `ft_absent`, the number of MPs who were absent for each ballot is stored as `r class(ballot_results_ft$ft_absent)` variable with values of the type `r typeof(ballot_results_ft$ft_absent)`.

The number of absentees for each observation is calculated by substracting the sum of `ballot_results_ft$ft_for`, `ballot_results_ft$ft_against` and `ballot_results_ft$ft_abstention` from `179`, the fixed number of MPs in Folketinget.

The maximum value stored in `ft_absent` is `r max(ballot_results_ft$ft_absent, na.rm = TRUE)` and the minimum value stored in `ft_absent` is `r min(ballot_results_ft$ft_absent, na.rm = TRUE)`. As the total number of MPs in Folketinget is 179, the value of `ft_absent` cannot be greater than `179`.

```{r}
summary(ballot_results_ft$ft_absent)
```

#### ballot_results_ft\$ft_process_id {#ballot_results_ftft_process_id}

All legislative processes in Folketinget are assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each process ID is thus a unique identifier for one process relating to legislation in Folketinget. All IDs are stored as values of the type `r typeof(ballot_results_ft$ft_process_id)` as `r class(ballot_results_ft$ft_process_id)` variable.

This variable corresponds to the [`sagstrinid`](#ballot_info_rawsagstrinid) variable and the `Sagstrin` resource in [the Folketing online database](https://oda.ft.dk).

`ft_process_id` used to join [`ballot_topics_raw`](#ballot_topics_raw) to [`northatlantic_ft`](#northatlantic_ft).

```{r}
head(ballot_results_ft$ft_process_id)
```

#### ballot_results_ft\$ballot_nr {#ballot_results_ftballot_nr}

In addition to the [`ballot_id`](#ballot_results_ftballot_id), all ballot procedures in Folketinget are also assigned a number by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each ballot number is thus another identifier for one ballot in Folketinget. All ballot numbers are stored as values of the type `r typeof(ballot_results_ft$ballot_nr)` as `r class(ballot_results_ft$ballot_nr)` variable.

This variable corresponds to the [`ballot_info_raw$nummer`](#ballot_info_rawnummer) variable in the `Afstemning` resource in [the Folketing online database](https://oda.ft.dk). Take care not to confuse `ballot_nr` with [`ballot_id`](#ballot_results_ftballot_id).

```{r}
head(ballot_results_ft$ballot_nr)
```

#### ballot_results_ft\$ballot_type_id {#ballot_results_ftballot_type_id}

All ballot procedures in Folketinget are categorised using numeric values that correspond to the type of ballot (@tbl-ballottypeid). All Ballot Type IDs are stored as values of the type `r typeof(ballot_results_ft$ballot_type_id)` as `r class(ballot_results_ft$ballot_type_id)` variable.

| ID | Type | English | n |
|:-----------------|:-----------------|:------------------|-----------------:|
| 1 | Endelig vedtagelse | Final Adoption | `r length(ballot_results_ft$ballot_type_id[ballot_results_ft$ballot_type_id == "1"])` |
| 2 | Udvalgsindstilling | Committee Recommendation Report | `r length(ballot_results_ft$ballot_type_id[ballot_results_ft$ballot_type_id == "2"])` |
| 3 | Forslag til vedtagelse | Proposed Adoption | `r length(ballot_results_ft$ballot_type_id[ballot_results_ft$ballot_type_id == "3"])` |
| 4 | Ændringsforslag | Amendment | `r length(ballot_results_ft$ballot_type_id[ballot_results_ft$ballot_type_id == "4"])` |

: Ballot Type IDs as used by Folketingets Open Data Service {#tbl-ballottypeid} {.striped .hover}

This variable corresponds to `typeid` variable in [`ballot_info_raw`](#ballot_info_rawtypeid) and the `type` variable in the `Afstemningstype` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
table(ballot_results_ft$ballot_type_id)
```

#### ballot_results_ft\$comment {#ballot_results_ftcomment}

If necessary, comments on each ballot are stored as values of the type `r typeof(ballot_results_ft$comment)` in Danish language. A Folketing wording standard for `comment` does not seem to exist, so the sentence structures and vocabulary differs a lot between observations. As per `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`, there are `r sum(!is.na(ballot_results_ft$comment))` observations with comments (total number of observations: `r nrow(ballot_results_ft)`). Comments on ballot results mostly regard human or technical errors, for example:

| Danish | English |
|--------------------------------|----------------------------------------|
| Ved en fejl er der ikke registreret stemmeafgivning fra X’ plads. | By mistake, no vote was registeret at X’ seat. |
| Ved en fejl stemte X for/imod/hverken for eller imod forslaget. | By mistake, X voted for/against/neither for nor against the proposal. |
| Ved en fejl har X ikke fået stemt. | By mistake, X could not vote. |
| Ved en fejl fik X ikke afgivet sin stemme. | By mistake, X could not cast a vote. |
| Ved en fejl er Xs stemme registeret i Ys navn. | By mistake, X’ vote was registered as a vote by Y. |
| X stemte ved en fejl fra Y’s plads. | By mistake, X voted from Y’s seat. |
| 10 i X stemte ved en fejl for/imod/hverken for eller imod forslaget. | By mistake, 10 MPs from party X voted for/against/neither for nor against the proposal. |
| Ved en fejl er der registreret en stemme på X. | By mistake, a vote by X was recorded. |
| X undlod ved en fejl at stemme. | By mistake, X did not cast a vote. |
| Omafstemning | Voting Repeated |

: {.striped .hover}

```{r}
head(ballot_results_ft$comment)
```

#### ballot_results_ft\$ballot_result_string {#ballot_results_ftballot_result_string}

In `ballot_result_string`, ballot results are stored as values of the type `r typeof(ballot_results_ft$ballot_result_string)` in Danish language. The variable indicates whether the proposal was adopted or not; how many votes were in favor resp. against or abstentions, and from which political parties these votes came. A Folketing wording standard for `ballot_result_string` does not seem to exist, so the sentence structures and vocabulary differs a lot between observations.

As per `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`, there are `r sum(!is.na(ballot_results_ft$ballot_result_string))` observations with result character strings (total number of observations: `r nrow(ballot_results_ft)`). For the observations where `ballot_result_string` is not `NA`, the values are used to calculate [`ft_for`](#ballot_results_ftft_for), [`ft_against`](#ballot_results_ftft_against) and [`ft_abstention`](#ballot_results_ftft_abstention). Information on absent MPs is not provided in `ballot_result_string` but [can be inferred from the other values](#ballot_results_ftft_absent).

```{r}
head(ballot_results_ft$ballot_result_string)
```

------------------------------------------------------------------------

### ballot_info_raw {#ballot_info_raw}

`ballot_info_raw` is provided as `rds` file in `/data/raw/`. It contains the downloaded data on voting records before any preprocessing. The [processed data](#ballot_results_ft) is available as `rds` file in `/data/processed`. As per `r format(file.info(here("data", "raw", "ballot_info_raw.rds"))$mtime, "%B %Y")`, `ballot_info_raw.rds` contains `r nrow(ballot_info_raw)` observations of `r ncol(ballot_info_raw)` variables.

```{r}
str(ballot_info_raw)
```

Descriptions of all variables in `ballot_info_raw` are provided in the following sections.

#### ballot_info_raw\$id {#ballot_info_rawid}

See [ballot_result_ft\$ballot_id](#ballot_results_ftballot_id). Take care not to confuse `id` with [`nummer`](#ballot_info_rawnummer). In the raw data, `id` is stored as `r typeof(ballot_info_raw$id)` value.

```{r}
head(ballot_info_raw$id)
```

#### ballot_info_raw\$nummer {#ballot_info_rawnummer}

See [ballot_results_ft\$ballot_nr](#ballot_results_ftballot_nr). Take care not to confuse `nummer` with [`id`](#ballot_info_rawid). In the raw data, `nummer` is stored as `r typeof(ballot_info_raw$nummer)` value.

```{r}
head(ballot_info_raw$nummer)
```

#### ballot_info_raw\$konklusion

See [ballot_results_ft\$ballot_result_string](#ballot_results_ftballot_result_string). In the raw data, `konklusion` is stored as `r typeof(ballot_info_raw$konklusion)` value.

```{r}
head(ballot_info_raw$konklusion)
```

#### ballot_info_raw\$vedtaget {#ballot_info_rawvedtaget}

See [ballot_results_ft\$ballot_pass](#ballot_results_ftballot_pass). In the raw data, `vedtaget` is stored as `r typeof(ballot_info_raw$vedtaget)` value.

```{r}
summary(ballot_info_raw$vedtaget)
```

#### ballot_info_raw\$kommentar

See [ballot_results_ft\$comment](#ballot_results_ftcomment). In the raw data, `kommentar` is stored as `r typeof(ballot_info_raw$kommentar)` value.

```{r}
head(ballot_info_raw$kommentar)
```

#### ballot_info_raw\$mødeid {#ballot_info_rawmødeid}

See [ballot_results_ft\$meeting_id](#ballot_results_ftmeeting_id). In the raw data, `mødeid` is stored as `r typeof(ballot_info_raw$mødeid)` value.

```{r}
head(ballot_info_raw$mødeid)
```

#### ballot_info_raw\$typeid {#ballot_info_rawtypeid}

See [ballot_results_ft\$ballot_type_id](#ballot_results_ftballot_type_id). In the raw data, `typeid` is stored as `r typeof(ballot_info_raw$typeid)` value.

```{r}
table(ballot_info_raw$typeid)
```

#### ballot_info_raw\$sagstrinid {#ballot_info_rawsagstrinid}

See [ballot_results_ft\$ft_process_id](#ballot_results_ftft_process_id). In the raw data, `sagstrinid` is stored as `r typeof(ballot_info_raw$sagstrinid)` value.

```{r}
head(ballot_info_raw$sagstrinid)
```

#### ballot_info_raw\$opdateringsdato

For all records kept in [the Folketing online database](https://oda.ft.dk), the time stamp of its most recent update is stored in `opdateringsdato`. All dates are stored as values of the type `r typeof(ballot_info_raw$opdateringsdato)`. The time stamps are formatted as `%Y-%m-%dT%T`, with some values even at split second level.

This variable is eliminated from [`ballot_results_ft`](#ballot_results_ft) as a result of data processing.

```{r}
head(ballot_info_raw$opdateringsdato)
```

------------------------------------------------------------------------

### ballot_topics_raw {#ballot_topics_raw}

`ballot_topics_raw` is provided as `rds` file in `/data/raw/`. It contains information on the content of each ballot in this data set, including the content of the proposal at hand. As per `r format(file.info(here("data", "raw", "ballot_topics_raw.rds"))$mtime, "%B %Y")`, `ballot_topics_raw.rds` contains `r nrow(ballot_topics_raw)` observations of `r ncol(ballot_topics_raw)` variables.

```{r}
str(ballot_topics_raw)
```

Descriptions of all variables in `ballot_topics_raw` are provided in the following sections.

#### ballot_topics_raw\$ft_process_id

All legislative processes in Folketinget are assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each process ID is thus a unique identifier for one process relating to legislation in Folketinget. All IDs are stored as values of the type `r typeof(ballot_topics_raw$ft_process_id)` as `r class(ballot_topics_raw$ft_process_id)` variable.

This variable corresponds to the [`sagstrinid`](#ballot_info_rawsagstrinid) variable and the `Sagstrin` resource in [the Folketing online database](https://oda.ft.dk).

`ft_process_id` is used to join `ballot_topics_raw` to [`northatlantic_ft`](#northatlantic_ft) based on matching with[`ballot_results_ft$ft_process_id`](#ballot_results_ftft_process_id).

```{r}
head(ballot_topics_raw$ft_process_id)
```

#### ballot_topics_raw\$ft_process_step {#ballot_topicsrawft_process_step}

All legislative processes in Folketinget run their course through Folketinget in several steps which is described by `ft_process_step`. Process steps are stored as values of the type `r typeof(ballot_topics_raw$ft_process_step)` in Danish language as `r class(ballot_topics_raw$ft_process_step)` variable.

This variable corresponds to the `titel` variable in the `Sagstrin` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
head(ballot_topics_raw$ft_process_step)
```

#### ballot_topics_raw\$ft_topic_id {#ballot_topicsrawft_topic_id}

Each proposal that is being voted on in Folketinget is assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data) based on the proposal's topic. Each topic ID is thus a unique identifier for one topic relating to several ballots and debates etc. in Folketinget. This identifier is stored in `ft_topic_id`. Topic IDs are stored as values of the type `r typeof(ballot_topics_raw$ft_topic_id)` as `r class(ballot_topics_raw$ft_topic_id)` variable.

This variable corresponds to the `id` variable in the `Sag` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
head(ballot_topics_raw$ft_topic_id)
```

#### ballot_topics_raw\$ft_topic {#ballot_topicsrawft_topic}

Each proposal that is being voted on in Folketinget has a description of the topic(s) that are mentioned in the proposal. This description is stored in `ft_topic`. Topic descriptions are stored as values of the type `r typeof(ballot_topics_raw$ft_topic)`.

This variable corresponds to the `titel` variable in the `Sag` resource in [the Folketing online database](https://oda.ft.dk) (which additionally provides a shorter version with less formalised language in the `titelkort` variable).

```{r}
head(ballot_topics_raw$ft_topic)
```

------------------------------------------------------------------------

### cabinets_fo {#cabinets_fo}

`cabinets_fo` is provided as both `rds` file in `/data/processed` and `csv` file in `/data/processed/csv`. Metadata for the `csv` file is provided in an accompanying `json` metadata file. The dataset contains information on the coalition governments of the Faroe Islands (Landsstýri), in particular a timeline including the parties that are part of each cabinet. As per `r format(file.info(here("data", "processed", "csv", "cabinets_fo.csv"))$mtime, "%B %Y")`, `cabinets_fo` contains information on `r nrow(cabinets_fo)` cabinets stored in `r ncol(cabinets_fo)` variables. This data set spans the timeframe covered by the voting database -- from `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")` until the most recent update of this data set on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`.

See also [cabinets_gl](#cabinets_gl) and [cabinets_dk](#cabinets_dk).

```{r}
str(cabinets_fo)
```

Descriptions of all variables in `cabinets_fo` are provided in the following sections.

#### cabinets_fo\$cabinet {#cabinets_focabinet}

Each cabinet formed in the Faroe Islands (Landsstýri) is assigned a human-readable identifier. The cabinets are usually named after the head of government, using their surname(s), followed by an integer number for multiple cabinets headed by the same person. Because in the timeframe covered by this data set, there have been two Faroese governments with a PM named Johannesen, the first letter of their first name is also appended to the `cabinet` variable. This variable is stored as value of the type `r typeof(cabinets_fo$cabinet)` as `r class(cabinets_fo$cabinet)` variable.

```{r}
head(cabinets_fo$cabinet)
```

#### cabinets_fo\$wikidata_id {#cabinets_fowikidata_id}

The `wikidata_id` variable stores the `QID` linking to the Wikidata entity representing the cabinet in question, making it easy to retrieve additional information from Wikidata, if necessary. This variable is stored as value of the type `r typeof(cabinets_fo$wikidata_id)` as `r class(cabinets_fo$wikidata_id)` variable.

```{r}
head(cabinets_fo$wikidata_id)
```

#### cabinets_fo\$location {#cabinets_folocation}

`location` indicates where a cabinet is formed -- in the Faroe Islands (`FO`). This variable is stored as value of the type `r typeof(cabinets_fo$location)` as `r class(cabinets_fo$location)` variable. When merging data, this proved to be helpful to distinguish between the different political parties, some of which share a common abbreviation across regions.

```{r}
table(cabinets_fo$location)
```

#### cabinets_fo\$start {#cabinets_fostart}

The date on which each cabinet is formed is stored as `r class(cabinets_fo$start)` variable of the type `r typeof(cabinets_fo$start)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_fo$start), "%B %d, %Y")` (`r min(cabinets_fo$start)`) and the most recent entry from `r format(max(cabinets_fo$start), "%B %d, %Y")` (`r max(cabinets_fo$start)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_fo.csv"))$mtime, "%B %Y")`.

```{r}
head(cabinets_fo$start)
```

#### cabinets_fo\$end {#cabinets_fo_end}

The date on which each cabinet is succeeded by the next one is stored as `r class(cabinets_fo$end)` variable of the type `r typeof(cabinets_fo$end)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_fo$end), "%B %d, %Y")` (`r min(cabinets_fo$end)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_fo.csv"))$mtime, "%B %Y")`.

Note that this date does not necessarily correspond to the date when a government 'collapses' or officially announces its resignation. Rather, the date denotes the day of the transition of power to the next cabinet.

```{r}
head(cabinets_fo$end)
```

#### cabinets_fo\$FO_A {#cabinets_fofoa}

`FO_A` indicates whether the Faroese political party **Fólkaflokkurin** (`A`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_A)` as `r class(cabinets_fo$FO_A)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_A` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_A)
```

#### cabinets_fo\$FO_B {#cabinets_fofob}

`FO_B` indicates whether the Faroese political party **Sambandsflokkurin** (`B`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_B)` as `r class(cabinets_fo$FO_B)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_B` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_B)
```

#### cabinets_fo\$FO_C {#cabinets_fofoc}

`FO_C` indicates whether the Faroese political party **Javnaðarflokkurin** (`C`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_C)` as `r class(cabinets_fo$FO_C)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_C` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_C)
```

#### cabinets_fo\$FO_D {#cabinets_fofod}

`FO_D` indicates whether the Faroese political party **Sjálvstýri** (`D`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_D)` as `r class(cabinets_fo$FO_D)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_D` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_D)
```

#### cabinets_fo\$FO_E {#cabinets_fofoe}

`FO_E` indicates whether the Faroese political party **Tjóðveldi** (`E`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_E)` as `r class(cabinets_fo$FO_E)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_E` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_E)
```

#### cabinets_fo\$FO_F {#cabinets_fofof}

`FO_F` indicates whether the Faroese political party **Framsókn** (`F`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_F)` as `r class(cabinets_fo$FO_F)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_F` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_F)
```

#### cabinets_fo\$FO_H {#cabinets_fofoh}

`FO_H` indicates whether the Faroese political party **Miðflokkurin** (`H`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_H)` as `r class(cabinets_fo$FO_H)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_H` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_H)
```

------------------------------------------------------------------------

### cabinets_gl {#cabinets_gl}

`cabinets_gl` is provided as both `rds` file in `/data/processed` and `csv` file in `/data/processed/csv`. Metadata for the `csv` file is provided in an accompanying `json` metadata file. The dataset contains information on the coalition governments of Greenland (Naalakersuisut), in particular a timeline including the parties that are part of each cabinet. As per `r format(file.info(here("data", "processed", "csv", "cabinets_gl.csv"))$mtime, "%B %Y")`, `cabinets_gl` contains information on `r nrow(cabinets_gl)` cabinets stored in `r ncol(cabinets_gl)` variables. This data set spans the timeframe covered by the voting database -- from `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")` until the most recent update of this data set on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`.

See also [cabinets_fo](#cabinets_fo) and [cabinets_dk](#cabinets_dk).

```{r}
str(cabinets_gl)
```

Descriptions of all variables in `cabinets_gl` are provided in the following sections.

#### cabinets_gl\$cabinet {#cabinets_glcabinet}

Each cabinet formed in Greenland (Naalakkersuisut) is assigned a human-readable identifier. The cabinets are usually named after the head of government, using their surname(s), followed by an integer number for multiple cabinets headed by the same person. Because in the timeframe covered by this data set, there have been two Faroese governments with a PM named Johannesen, the first letter of their first name is also appended to the `cabinet` variable. This variable is stored as value of the type `r typeof(cabinets_gl$cabinet)` as `r class(cabinets_gl$cabinet)` variable.

```{r}
head(cabinets_gl$cabinet)
```

#### cabinets_gl\$wikidata_id {#cabinets_glwikidata_id}

The `wikidata_id` variable stores the `QID` linking to the Wikidata entity representing the cabinet in question, making it easy to retrieve additional information from Wikidata, if necessary. This variable is stored as value of the type `r typeof(cabinets_gl$wikidata_id)` as `r class(cabinets_gl$wikidata_id)` variable.

```{r}
head(cabinets_gl$wikidata_id)
```

#### cabinets_gl\$location {#cabinets_gllocation}

`location` indicates where a cabinet is formed -- in Greenland (`GL`). This variable is stored as value of the type `r typeof(cabinets_gl$location)` as `r class(cabinets_gl$location)` variable. When merging data, this proved to be helpful to distinguish between the different political parties, some of which share a common abbreviation across regions.

```{r}
table(cabinets_gl$location)
```

#### cabinets_gl\$start {#cabinets_glstart}

The date on which each cabinet is formed is stored as `r class(cabinets_gl$start)` variable of the type `r typeof(cabinets_gl$start)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_gl$start), "%B %d, %Y")` (`r min(cabinets_gl$start)`) and the most recent entry from `r format(max(cabinets_gl$start), "%B %d, %Y")` (`r max(cabinets_gl$start)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_gl.csv"))$mtime, "%B %Y")`.

```{r}
head(cabinets_gl$start)
```

#### cabinets_gl\$end {#cabinets_glend}

The date on which each cabinet is succeeded by the next one is stored as `r class(cabinets_gl$end)` variable of the type `r typeof(cabinets_gl$end)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_gl$end), "%B %d, %Y")` (`r min(cabinets_gl$end)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_gl.csv"))$mtime, "%B %Y")`.

Note that this date does not necessarily correspond to the date when a government 'collapses' or officially announces its resignation. Rather, the date denotes the day of the transition of power to the next cabinet.

```{r}
head(cabinets_gl$end)
```

#### cabinets_gl\$GL_A {#cabinets_glgla}

`GL_A` indicates whether the Greenlandic political party **Atassut** (`A`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_A)` as `r class(cabinets_gl$GL_A)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_A` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_A)
```

#### cabinets_gl\$GL_D {#cabinets_glgld}

`GL_D` indicates whether the Greenlandic political party **Demokraatit** (`D`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_D)` as `r class(cabinets_gl$GL_D)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_D` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_D)
```

#### cabinets_gl\$GL_IA {#cabinets_glglia}

`GL_IA` indicates whether the Greenlandic political party **Inuit Ataqatigiit** (`IA`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_IA)` as `r class(cabinets_gl$GL_IA)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_IA` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_IA)
```

#### cabinets_gl\$GL_KP {#cabinets_glglkp}

`GL_KP` indicates whether the Greenlandic political party **Kattusseqatigiit Partiiat** (`KP`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_KP)` as `r class(cabinets_gl$GL_KP)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_KP` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_KP)
```

#### cabinets_gl\$GL_N {#cabinets_glgln}

`GL_N` indicates whether the Greenlandic political party **Naleraq** (`N`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_N)` as `r class(cabinets_gl$GL_N)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_N` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_N)
```

#### cabinets_gl\$GL_NQ {#cabinets_glglnq}

`GL_NQ` indicates whether the Greenlandic political party **Nunatta Qitornai** (`NQ`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_NQ)` as `r class(cabinets_gl$GL_NQ)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_NQ` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_NQ)
```

#### cabinets_gl\$GL_PI {#cabinets_glglpi}

`GL_PI` indicates whether the Greenlandic political party **Partii Inuit** (`PI`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_PI)` as `r class(cabinets_gl$GL_PI)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_PI` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_PI)
```

#### cabinets_gl\$GL_SIU {#cabinets_glglsiu}

`GL_SIU` indicates whether the Greenlandic political party **Siumut** (`SIU`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_SIU)` as `r class(cabinets_gl$GL_SIU)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_SIU` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_SIU)
```

------------------------------------------------------------------------

### cabinets_dk {#cabinets_dk}

`cabinets_dk` is provided as `csv` and `rds` file in `/data/processed/`. Metadata for the `csv` file is provided in an accompanying `json` metadata file. The dataset contains information on coalition governments of Denmark, in particular a timeline including the parties that are part of each cabinet. As per `r format(file.info(here("data", "processed", "csv", "cabinets_dk.csv"))$mtime, "%B %Y")`, `cabinets_dk` contains information on `r nrow(cabinets_dk)` cabinets stored in `r ncol(cabinets_dk)` variables. On this list are `r sum(cabinets_dk$bloc == "left", na.rm = TRUE)` red bloc/left-wing, `r sum(cabinets_dk$bloc == "right", na.rm = TRUE)` blue/right-wing and `r sum(cabinets_dk$bloc == "across", na.rm = TRUE)` cross-bloc cabinets. This data set spans the timeframe covered by the voting database -- from `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")` until the most recent update of this data set on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`.

See also [cabinets_fo](#cabinets_fo) and [cabinets_gl](#cabinets_gl).

```{r}
str(cabinets_dk)
```

Descriptions of all variables in `cabinets_dk` are provided in the following sections.

#### cabinets_dk\$cabinet {#cabinets_dkcabinet}

Each cabinet formed in Denmark is assigned a human-readable identifier. The cabinets are usually named after the head of government, using their surname(s), followed by an integer number for multiple cabinets headed by the same person. Because in the timeframe covered by this data set, there have been two Danish governments with a PM named Rasmussen, the first letter of their first name is also appended to the `cabinet` variable. This variable is stored as value of the type `r typeof(cabinets_dk$cabinet)` as `r class(cabinets_dk$cabinet)` variable.

```{r}
head(cabinets_dk$cabinet)
```

#### cabinets_dk\$wikidata_id {#cabinets_dkwikidata_id}

The `wikidata_id` variable stores the `QID` linking to the Wikidata entity representing the cabinet in question, making it easy to retrieve additional information from Wikidata, if necessary. This variable is stored as value of the type `r typeof(cabinets_dk$wikidata_id)` as `r class(cabinets_dk$wikidata_id)` variable.

```{r}
head(cabinets_dk$wikidata_id)
```

#### cabinets_dk\$bloc {#cabinets_dkbloc}

`bloc` indicates whether a cabinet belongs to either the red/left or blue/right section of the political spectrum or if it is formed across both blocs. This variable is stored as value of the type `r typeof(cabinets_dk$bloc)` as `r class(cabinets_dk$bloc)` variable.

```{r}
table(cabinets_dk$bloc)
```

#### cabinets_dk\$type {#cabinets_dktype}

`type` indicates whether a cabinet is formed by a single politial party or if it is a coalition government. This variable is stored as value of the type `r typeof(cabinets_dk$type)` as `r class(cabinets_dk$type)` variable.

Note that a `single_party` cabinet does not necessarily have the majority of seats in parliament. The cabinet in question may instead rely on informal support agreements with other political parties that are not officially part of the cabinet.

```{r}
table(cabinets_dk$type)
```

#### cabinets_dk\$start {#cabinets_dkstart}

The date on which each cabinet is formed is stored as `r class(cabinets_dk$start)` variable of the type `r typeof(cabinets_dk$start)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_dk$start), "%B %d, %Y")` (`r min(cabinets_dk$start)`) and the most recent entry from `r format(max(cabinets_dk$start), "%B %d, %Y")` (`r max(cabinets_dk$start)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_dk.csv"))$mtime, "%B %Y")`.

```{r}
head(cabinets_dk$start)
```

#### cabinets_dk\$end {#cabinets_dkend}

The date on which each cabinet is succeeded by the next one is stored as `r class(cabinets_dk$end)` variable of the type `r typeof(cabinets_dk$end)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_dk$end), "%B %d, %Y")` (`r min(cabinets_dk$end)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_dk.csv"))$mtime, "%B %Y")`.

Note that this date does not necessarily correspond to the date when a government 'collapses' or officially announces its resignation. Rather, the date denotes the day of the transition of power to the next cabinet.

```{r}
head(cabinets_dk$end)
```

#### cabinets_dk\$DK_A {#cabinets_dkdka}

`DK_A` indicates whether the Danish political party **Socialdemokratiet** (`A`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_A)` as `r class(cabinets_dk$DK_A)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_A` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_A)
```

#### cabinets_dk\$DK_B {#cabinets_dkdkb}

`DK_B` indicates whether the Danish political party **Radikale Venstre** (`B`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_B)` as `r class(cabinets_dk$DK_B)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_B` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_B)
```

#### cabinets_dk\$DK_C {#cabinets_dkdkc}

`DK_C` indicates whether the Danish political party **Det Konservative Folkeparti** (`C`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_C)` as `r class(cabinets_dk$DK_C)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_C` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_C)
```

#### cabinets_dk\$DK_F {#cabinets_dkdkf}

`DK_F` indicates whether the Danish political party **Socialistisk Folkeparti** (`F`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_F)` as `r class(cabinets_dk$DK_F)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_F` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_F)
```

#### cabinets_dk\$DK_I {#cabinets_dkdki}

`DK_I` indicates whether the Danish political party **Liberal Alliance** (`I`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_I)` as `r class(cabinets_dk$DK_I)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_I` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_I)
```

#### cabinets_dk\$DK_M {#cabinets_dkdkm}

`DK_M` indicates whether the Danish political party **Moderaterne** (`M`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_M)` as `r class(cabinets_dk$DK_M)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_M` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_M)
```

#### cabinets_dk\$DK_V {#cabinets_dkdkv}

`DK_V` indicates whether the Danish political party **Venstre** (`V`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_V)` as `r class(cabinets_dk$DK_V)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_V` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_V)
```

------------------------------------------------------------------------

### northatlantic_ft {#northatlantic_ft}

`northatlantic_ft` is the resulting product of the [targets pipeline](/_targets.R) and is provided as both `rds` file in `/data/processed` and `csv` file in `/data/processed/csv`. Metadata for the `csv` file is provided in an accompanying `json` metadata file. The dataset contains data on voting records of the MPs specified in [`MP_names`](#mp_names), created by processing and joining [`ballot_results_ft`](#ballot_results_ft), [`northatlantic_votes`](#northatlantic_votes), [`ballot_topics_raw`](#ballot_topics_raw) as well as information on cabinets from [`cabinets_fo`](#cabinets_fo), [`cabinets_gl`](#cabinets_gl) and [`cabinets_dk`](#cabinets_dk) and on MP membership timelines from [`MP_dates`](#mp_dates). As per `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %Y")`, `northatlantic_ft` contains `r nrow(northatlantic_ft)` observations of `r ncol(northatlantic_ft)` variables.

```{r}
str(northatlantic_ft)
```

Descriptions of all variables in `northatlantic_ft` are provided in the following sections.

#### northatlantic_ft\$ballot_id

`ballot_id` is created by using [`join_results()`](/src/targets/join_results.R) on `northatlantic_votes` and `ballot_results_ft`. See [`northatlantic_votes$ballot_id`](#northatlantic_votesballot_id).

```{r}
str(northatlantic_ft$ballot_id)
```

#### northatlantic_ft\$MP_id

`MP_id` is created by using [`join_results()`](/src/targets/join_results.R) on `northatlantic_votes` and `ballot_results_ft`. See [`northatlantic_votes$MP_id`](#northatlantic_votesmp_id).

```{r}
str(northatlantic_ft$MP_id)
```

#### northatlantic_ft\$surname

`surname` is created by using [`join_results()`](/src/targets/join_results.R) on `northatlantic_votes`, `ballot_results_ft`, and `MP_names`. See [`MP_names$surname`](#mp_namessurname).

```{r}
str(northatlantic_ft$surname)
```

#### northatlantic_ft\$origin

`origin` is created by using [`join_results()`](/src/targets/join_results.R) on `northatlantic_votes`, `ballot_results_ft`, and `MP_names`. See [`MP_names$origin`](#mp_namesorigin).

```{r}
summary(northatlantic_ft$origin)
```

#### northatlantic_ft\$party

`party` is created by using [`match_party_affiliation()`](/src/targets/match_party_affiliation.R), combining [`northatlantic_ft$ballot_date`](#northatlantic_ftballot_date) and [`MP_dates`](#mp_dates). This way, changes in party affiliations are reflected in `northatlantic_ft$party` as well.

```{r}
summary(northatlantic_ft$party)
```

#### northatlantic_ft\$gvt_party_at_home

`gvt_party_at_home` is created by using [`match_home_government()`](/src/targets/match_home_government.R) on `northatlantic_ft`, and `cabinets_fo` resp. `cabinets_gl`, indicating whether the MP is a member of a political party that is part of the governing Naalakkersuisut (GL) resp. Landsstýri (FO) at the time. See [`cabinets_fo`](#cabinets_fo) and [`cabinets_gl`](#cabinets_gl).

```{r}
summary(northatlantic_ft$gvt_party_at_home)
```

#### northatlantic_ft\$vote_type_id

`northatlantic_ft` is a result of [`join_results()`](/src/targets/join_results.R) in which `vote_type_id` is joined from `northatlantic_votes$vote_type_id`. See [`northatlantic_votes$vote_type_id`](#northatlantic_votesvote_type_id).

```{r}
table(northatlantic_ft$vote_type_id)
```

#### northatlantic_ft\$vote_id

See [`northatlantic_votes$votes_id`](#northatlantic_votesvote_id).

```{r}
str(northatlantic_ft$vote_id)
```

#### northatlantic_ft\$ballot_pass

See [`ballot_results_ft$ballot_pass`](#ballot_results_ftballot_pass).

```{r}
summary(northatlantic_ft$ballot_pass)
```

#### northatlantic_ft\$ft_process_step

See [`ballot_topics_raw$ft_process_step`](#ballot_topics_rawft_process_step).

```{r}
str(northatlantic_ft$ft_process_step)
```

#### northatlantic_ft\$ft_topic_id

See [`ballot_topics_raw$ft_topic_id`](#ballot_topics_rawft_topic_id).

```{r}
head(northatlantic_ft$ft_topic_id)
```

#### northatlantic_ft\$ft_topic

See [`ballot_topics_raw$ft_topic`](#ballot_topics_rawft_topic).

```{r}
str(northatlantic_ft$ft_topic)
```

#### northatlantic_ft\$ft_for

See [`ballot_results_ft$ft_for`](#ballot_results_ftft_for).

```{r}
summary(northatlantic_ft$ft_for)
```

#### northatlantic_ft\$ft_against

See [`ballot_results_ft$ft_against`](#ballot_results_ftft_against).

```{r}
summary(northatlantic_ft$ft_against)
```

#### northatlantic_ft\$ft_abstention

See [`ballot_results_ft$ft_abstention`](#ballot_results_ftft_abstention).

```{r}
summary(northatlantic_ft$ft_abstention)
```

#### northatlantic_ft\$ft_absent

See [`ballot_results_ft$ft_absent`](#ballot_results_ftft_absent).

```{r}
summary(northatlantic_ft$ft_absent)
```

#### northatlantic_ft\$ballot_date {#northatlantic_ftballot_date}

See [`ballot_results_ft$ballot_date`](#ballot_results_ftballot_date).

```{r}
str(northatlantic_ft$ballot_date)
```

#### northatlantic_ft\$ballot_type_id

See [`ballot_results_ft$ballot_type_id`](#ballot_results_ftballot_type_id).

```{r}
table(northatlantic_ft$ballot_type_id)
```

#### northatlantic_ft\$gvt_type_dk

`gvt_type_dk` is created by using [`match_danish_government()`](/src/targets/match_danish_government.R) on [`cabinets_dk`](#cabinets_dk), indicating whether the Danish government is a coalition or a single-party government at the time of the observation. See [`cabinets_dk$type`](#cabinets_dktype).

```{r}
summary(northatlantic_ft$gvt_type_dk)
```

#### northatlantic_ft\$gvt_bloc_dk

`gvt_bloc_dk` is created by using [`match_danish_government()`](/src/targets/match_danish_government.R) on [`cabinets_dk`](#cabinets_dk), indicating the political bloc (left/red, right/blue or across) the Danish government belongs to at the time of the observation. See [`cabinets_dk$bloc`](#cabinets_dkbloc).

```{r}
summary(northatlantic_ft$gvt_bloc_dk)
```

#### northatlantic_ft\$comment

See [`ballot_results_ft$comment`](#ballot_results_ftcomment).

```{r}
str(northatlantic_ft$comment)
```

#### northatlantic_ft\$ballot_result_string

See [`ballot_results_ft$ballot_result_string`](#ballot_results_ftballot_result_string).

```{r}
str(northatlantic_ft$ballot_result_string)
```