---
title: Codebook neu
authors:
  - name: Moritz Twente
    affiliation: University of Basel
    email: moritz.twente@unibas.ch
    orcid: 0009-0005-7187-9774
date-modified: last-modified
bibliography: ../assets/nordatlantisk-ft.bib
link-citations: true
lang: en
---

```{r setup}
#| echo: false
#| message: false

# Setup -----
## Packages -----

library(here)
library(ggplot2)
library(dplyr)
library(readr)
library(knitr)
library(forcats)
library(lubridate)

## Read Data -----

### List of MPs -----
MP_names <- readRDS(here("data", "processed", "MP_names.rds"))

### List of political parties -----
political_parties <- readRDS(here("data", "processed", "political_parties.rds"))

### Voting Records Database -----
northatlantic_votes <- readRDS(here("data", "processed", "northatlantic_votes.rds"))
northatlantic_votes_raw <- readRDS(here("data", "raw", "northatlantic_votes_raw.rds"))
ballot_info_raw <- readRDS(here("data", "raw", "ballot_info_raw.rds"))
ballot_results_ft <- readRDS(here("data", "processed", "ballot_results_ft.rds"))

northatlantic_ft <- readRDS(here("data", "processed", "northatlantic_ft.rds"))

plot_dataset <- northatlantic_ft %>%
  left_join(MP_names %>% select(MP_id, origin), by = "MP_id")

### Timeline of MP_dates and Cabinets -----
MP_dates <- readRDS(here("data", "processed", "MP_dates.rds"))
election_dates <- readRDS(here("data", "processed", "election_dates.rds"))
cabinets_dk <- readRDS(here("data", "processed", "cabinets_dk.rds"))

cabinets_fo <- readRDS(here("data", "processed", "cabinets_fo.rds"))
cabinets_gl <- readRDS(here("data", "processed", "cabinets_gl.rds"))

#### Convert dates
MP_dates <- MP_dates %>%
  mutate(
    start = ymd(start),
    end   = ymd(end),
    # Replace NA in "end" with today's date
    end   = if_else(is.na(end), Sys.Date(), end)
  )

cabinets_fo <- cabinets_fo %>%
    mutate(
      start = ymd(start),
      end   = ymd(end),
      end   = coalesce(end, Sys.Date())
    )

cabinets_gl <- cabinets_gl %>%
    mutate(
      start = ymd(start),
      end   = ymd(end),
      end   = coalesce(end, Sys.Date())
    )

cabinets_dk <- cabinets_dk %>%
    mutate(
      start = ymd(start),
      end   = ymd(end),
      end   = coalesce(end, Sys.Date())
    )

cabinets_fo_gl <- full_join(cabinets_gl, cabinets_fo)

```

## Introduction {#introduction}

This codebook provides descriptions of the `nordatlantisk-ft` data set, i.e. of all files in `/data/`. Variables are described for each file individually with information on connections to other variables within the pipeline to create the data set. All data, unless otherwise specified, is retrieved from the records of the parliament of Denmark, @folketingetFolketingetsAbneData2025.

All data is available in `rds` format that can be read in an R Session via `readRDS()`. Where data is also available in `csv` format, tabular metadata is provided in `json` files according to the W3C Metadata Vocabulary for Tabular Data [@w3cW3CRecommendationMetadata2015].

## File and Variable Descriptions {#file-and-variable-descriptions}

The general structure of the data used in the workflow to compile the final `northatlantisk_ft.csv` output is illustrated in @fig-datamodel. Click on an element to jump to its description in the codebook.

```{mermaid datamodel}
%%| label: fig-datamodel
%%| fig-cap: Chart illustrating the files used to create the dataset including variable names and types.

classDiagram
    direction LR

    MP_dates .. MP_names
    MP_dates .. election_dates
    MP_dates .. political_parties

    MP_names *-- northatlantic_ft

    northatlantic_votes <|-- northatlantic_ft
    ballot_results_ft <|-- northatlantic_ft

    MP_names *-- northatlantic_votes_raw
    northatlantic_votes_raw <|-- northatlantic_votes

    ballot_info_raw <|-- ballot_results_ft

    cabinets_fo .. cabinets_gl
    cabinets_gl .. cabinets_dk
    cabinets_dk <|-- northatlantic_ft

    MP_dates *-- northatlantic_ft

    class northatlantic_ft {
        ballot_id : int
        MP_id : int
        surname : string
        origin: string
        party : string
        gvt_party_at_home: bool
        vote_type_id : int
        vote_id : int
        ballot_pass : bool
        ft_process_step : string
        ft_topic_id : int
        ft_topic : string
        ft_for : int
        ft_against : int
        ft_abstention : int
        ft_absent : int
        ballot_date : date
        ballot_type_id : int
        gvt_type_dk : string
        gvt_bloc_dk : string
        comment : string
        ballot_result_string : int
    }

        class northatlantic_votes {
        vote_id : int
        vote_type_id : int
        ballot_id : int
        MP_id : int
    }

        class MP_dates {
        period_id : string
        surname : string
        first_name : string
        MP_id: int
        origin: string
        party : string
        start : date
        end : date
        substitute : bool
    }

    class election_dates {
        election : string
        election_type : string
        date : date
    }

    class MP_names {
        surname : string
        first_name : string
        MP_id : int
        wikidata_id : string
        origin : string
        party : string
        substitute : bool
    }

    class ballot_results_ft {
        ballot_id : int
        meeting_id : int
        ballot_pass : bool
        ballot_date : date
        ft_topic: string
        ft_for : int
        ft_against : int
        ft_abstention : int
        ft_absent : int
        ft_process_id : int
        ft_process_step: string
        ballot_nr : int
        ballot_type_id : int
        comment : string
        ballot_result_string : string
    }

    class ballot_info_raw {
        id : int
        nummer : int
        konklusion : string
        vedtaget : bool
        kommentar : string
        mødeid : int
        typeid : int
        sagstrinid : int
        sagstrin_titel : string
        sag_titel : string
        dato : date
        opdateringsdato : date
    }

    class northatlantic_votes_raw {
        id : int
        typeid : int
        afstemningid : int
        aktørid : int
        opdateringsdato : date
    }

    class political_parties {
        party : string
        full_name : string
        wikidata_id : string
        party_family : string
        colour : string
        origin : string
        left_right : float
        state_market : float
        liberty_authority : float
        anti_pro_eu : float
    }

    class cabinets_fo {
      cabinet: string
      wikidata_id: string
      location: string
      start: date
      end: date
      FO_&ast;: bool
    }

    class cabinets_gl {
      cabinet: string
      wikidata_id: string
      location: string
      start: date
      end: date
      GL_&ast;: bool
    }

    class cabinets_dk {
      cabinet: string
      wikidata_id: string
      bloc: string
      type: string
      start: date
      end: date
      DK_&ast;: bool
    }

style ballot_info_raw fill:#6195CF,color:#FFFFFF
style ballot_results_ft fill:#6195CF,color:#FFFFFF

style northatlantic_ft fill:#F7CB45

style northatlantic_votes_raw fill:#FFEAAE
style northatlantic_votes fill:#FFEAAE

style MP_names fill:#D1BBD7
style MP_dates fill:#D1BBD7

click MP_dates href "#mp_dates" "tooltip"
click election_dates href "#election_dates" "tooltip"
click political_parties href "#political_parties" "tooltip"
click MP_names href "#MP_names" "tooltip"
click northatlantic_votes_raw href "#northatlantic_votes_raw" "tooltip"
click northatlantic_votes href "#northatlantic_votes" "tooltip"
click ballot_info_raw href "#ballot_info_raw" "tooltip"
click ballot_results_ft href "#ballot_results_ft" "tooltip"
click cabinets_fo href "#cabinets_fo" "tooltip"
click cabinets_gl href "#cabinets_gl" "tooltip"
click cabinets_dk href "#cabinets_dk" "tooltip"
click northatlantic_ft href "#northatlantic_ft" "tooltip"
```

------------------------------------------------------------------------

### MP_names

This repository is shipped with a list of all Folketinget MPs that have represented the Faroe Islands and Greenland from `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")` until the most recent update of this data set (on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`), which results in `r nrow(MP_names)` MPs.

`MP_names` is provided in `csv` and `rds` formats in `/data/processed`.  Metadata for the `csv` file is provided in an accompanying `json` metadata file. The `rds` file serves as starting point for building the data set, as the workflow pipeline[^1] retrieves data from [Folketingets Open Data Portal](https://oda.ft.dk) based on which MPs are listed in this file.

[^1]: See [README](/index.qmd) or [`_targets.R`](/_targets.R)

```{r MP_names-intro}
str(MP_names)
```

Descriptions of all variables in `MP_names` are provided in the following sections.

#### MP_names$surname

...

```{r MP_names-surname}
head(MP_names$surname)
```


#### MP_names$first_name

...

```{r MP_names-first_name}
head(MP_names$first_name)
```


#### MP_names$MP_id

...

```{r MP_names-MP_id}
head(MP_names$MP_id)
```


#### MP_names$wikidata_id

...

```{r MP_names-wikidata_id}
head(MP_names$wikidata_id)
```

#### MP_names$origin

...

```{r MP_names-origin}
summary(MP_names$origin)
```

#### MP_names$party

...

```{r MP_names-party}
summary(MP_names$party)
```

All represented political parties are listed in @tbl-parties with additional information (where available) on their positions from the ParlGov dataset [@doringParlGov2022Release2022].

```{r parties-list}
#| echo: false
#| message: false
#| label: tbl-parties
#| tbl-cap: List of political parties from Greenland and the Faroe Islands with a MP in Folketinget since 2004.

political_parties_printable <- political_parties |>
  mutate(
    full_name_linked = ifelse(
      is.na(wikidata_id) | wikidata_id == "",
      full_name,
      paste0("[", full_name, "](https://wikidata.org/wiki/", wikidata_id, ")")
    )
  )

parties_gl_printable <- political_parties_printable |>
  filter(origin == "GL") |>
  select(party, full_name_linked, party_family,
         left_right, state_market, liberty_authority, anti_pro_eu)

parties_fo_printable <- political_parties_printable |>
  filter(origin == "FO") |>
  select(party, full_name_linked, party_family,
         left_right, state_market, liberty_authority, anti_pro_eu)

printable_names <- c(
  "Party", "Full Name", "Party Family",
  "Left–Right", "State–Market", "Liberty–Authority", "Anti–Pro-EU"
)

kable(
  parties_gl_printable,
  caption = "Greenlandic Parties",
  col.names = printable_names,
  row.names = FALSE,
  escape = FALSE
)

kable(
  parties_fo_printable,
  caption = "Faroese Parties",
  col.names = printable_names,
  row.names = FALSE,
  escape = FALSE)
```

#### MP_names$substitute

...

```{r MP_names-substitute}
summary(MP_names$substitute)
```

------------------------------------------------------------------------

### MP_dates

The dataset includes detailed information on membership timelines of MPs in Folketinget. Because a substantial share of MPs from Greenland and the Faroe Islands were absent for a longer period [@harderFaeroskeOgGronlandske2022, 12-13], there have been a number of substitute MPs (stedfortrædere) replacing the originally elected politicians during their time(s) of absence. Those MPs are listed here as well. As of `r format(file.info(here("data", "processed", "csv", "MP_dates.csv"))$mtime, "%B %d, %Y")`, `MP_dates` includes `r nrow(MP_dates)` observations of `r ncol(MP_dates)` variables.

`MP_dates` is provided in `csv` and `rds` formats in `/data/processed`.  Metadata for the `csv` file is provided in an accompanying `json` metadata file. 


```{r MP_dates-intro}
str(MP_dates)
```

Descriptions of all variables in `MP_dates` are provided in the following sections.

#### MP_dates$period_id

...

```{r MP_dates-period_id}
str(MP_dates$period_id)
```

#### MP_dates$surname

...

```{r MP_dates-surname}
str(MP_dates$surname)
```


#### MP_dates$first_name

...

```{r MP_dates-first_name}
str(MP_dates$first_name)
```


#### MP_dates$MP_id

...

```{r}
str(MP_dates$MP_id)
```


#### MP_dates$origin

...

```{r MP_dates-origin}
summary(MP_dates$origin)
```


#### MP_dates$party

...

```{r MP_dates-party}
unique(MP_dates$party)
```


#### MP_dates$start

...

```{r MP_dates-start}
head(MP_dates$start)
```


#### MP_dates$end

...

```{r MP_dates-end}
head(MP_dates$end)
```


#### MP_dates$substitute

```{r MP_dates-substitute}
summary(MP_dates$substitute)
```

------------------------------------------------------------------------

### election_dates

This repository is shipped with a list of all elections to the parliaments in Denmark (Folketinget), Greenland (Inatsisartut) and the Faroe Islands (Løgtingið) that led to the formation of the parliaments in session during the time period covered by this data set. This translates to `r nrow(election_dates[election_dates$election_type == "Folketing Election",])` elections to Folketing, `r nrow(election_dates[election_dates$election_type == "Inatsisartut Election",])` elections to Inatsisartut, and `r nrow(election_dates[election_dates$election_type == "Løgting Election",])` elections to Løgting. The earliest election included is the one held on `r format(min(election_dates$date), "%B %d, %Y")`, while the most recent election included was held on `r format(max(election_dates$date), "%B %d, %Y")`.

The contents of `election_dates` is not used during the workflow to compile the final `northatlantik_ft` data set, but is used as secondary data for visualisation purposes.

`election_dates` is provided in `csv` and `rds` formats in `/data/processed`. Metadata for the `csv` file is provided in an accompanying `json` metadata file. These files are compiled by executing the script at [`src/create_election_list.R`](/src/create_election_list.R) and following elections should be added by updating this script.

```{r election_dates-intro}
str(election_dates)
```

Descriptions of all variables in `election_dates` are provided in the following sections.

#### election_dates$election

...

```{r election_dates-election}
head(election_dates$election)
```


#### election_dates$election_type

...

```{r election_dates-election_type}
summary(election_dates$election_type)
```



#### election_dates$date

...

```{r election_dates-date}
str(election_dates$date)
```

------------------------------------------------------------------------

### political_parties

This repository is shipped with a list of political parties that have been represented in Folketinget during the time period covered by this data set. This list was most recently updated on `r format(file.info(here("data", "processed", "csv", "political_parties.csv"))$mtime, "%B %d, %Y")` and includes `r nrow(political_parties)` political parties. From these parties, `r nrow(political_parties[political_parties$origin == "GL", ])` are from Greenland and `r nrow(political_parties[political_parties$origin == "FO", ])` from the Faroe Islands.

The contents of `election_dates` is not used during the workflow to compile the final `northatlantik_ft` data set, but is used as secondary data for visualisation purposes.

`political_parties` is provided is provided in `csv` and `rds` formats in `/data/processed`. Metadata for the `csv` file is provided in an accompanying `json` metadata file.

```{r political_parties-intro}
str(political_parties)
```

Descriptions of all variables in `political_parties` are provided in the following sections.

#### political_parties$party

...

```{r political_parties-party}
head(political_parties$party)
```

#### political_parties$full_name

...

```{r political_parties-full_name}
str(political_parties$full_name)
```

#### political_parties$wikidata_id

...

```{r}
head(political_parties$wikidata_id)
```

#### political_parties$party_family

...

```{r political_parties-party_family}
head(political_parties$party_family)
```

#### political_parties$colour

...

```{r political_parties-colour}
head(political_parties$colour)
```

#### political_parties$origin

...

```{r political_parties-origin}
summary(political_parties$origin)
```

#### political_parties$left_right

...

```{r political_parties-left_right}
head(political_parties$left_right)
```

#### political_parties$state_market

...

```{r political_parties-state_market}
head(political_parties$state_market)
```

#### political_parties$liberty_authority

...

```{r political_parties-liberty_authority}
head(political_parties$liberty_authority)
```

#### political_parties$anti_pro_eu

...

```{r political_parties-anti_pro_eu}
head(political_parties$anti_pro_eu)
```

------------------------------------------------------------------------

### northatlantic_votes

After all votes cast by the MPs specified in [`MP_names`](#mp_names) are downloaded, they are processed and then stored in this file. As per `r format(file.info(here("data", "processed", "northatlantic_votes.rds"))$mtime, "%B %Y")`, `northatlantic_votes.rds` contains `r nrow(northatlantic_votes)` observations of `r ncol(northatlantic_votes)` variables.

`northatlantic_votes` is provided as `rds` file in `/data/processed/`. The unprocessed [raw data](#northatlantic_votes_raw) is available as `rds` file in `/data/raw/`.

```{r northatlantic_votes-intro}
str(northatlantic_votes)
```

Descriptions of all variables in `northatlantic_votes` are provided in the following sections.

#### northatlantic_votes$vote_id

...

```{r northatlantic_votes-vote_id}
head(northatlantic_votes$vote_id)
```


#### northatlantic_votes$vote_type_id

...

```{r northatlantic_votes-vote_type_id}
head(northatlantic_votes$vote_type_id)
```


#### northatlantic_votes$ballot_id

...

```{r northatlantic_votes-ballot_id}
head(northatlantic_votes$ballot_id)
```


#### northatlantic_votes$MP_id

...

```{r northatlantic_votes-MP_id}
head(northatlantic_votes$MP_id)
```

------------------------------------------------------------------------


### northatlantic_votes_raw {#northatlantic_votes_raw}

`northatlantic_votes_raw` contains the downloaded data on voting records before any preprocessing. As of `r format(file.info(here("data", "raw", "northatlantic_votes_raw.rds"))$mtime, "%B %Y")`, `northatlantic_votes_raw.rds` contains `r nrow(northatlantic_votes_raw)` observations of `r ncol(northatlantic_votes_raw)` variables.

`northatlantic_votes_raw` is provided as `rds` file in `/data/raw/`. The [processed data](#northatlantic_votes) is available as `rds` file in `/data/processed`.

```{r northatlantic_votes_raw-intro}
str(northatlantic_votes_raw)
```

Descriptions of all variables in `northatlantic_votes_raw` are provided in the following sections.

#### northatlantic_votes_raw$id

...

```{r northatlantic_votes_raw-id}
head(northatlantic_votes_raw$id)
```

#### northatlantic_votes_raw$typeid

...

```{r northatlantic_votes_raw-typeid}
unique(northatlantic_votes_raw$typeid)
```

#### northatlantic_votes_raw$afstemningid

...

```{r northatlantic_votes_raw-afstemningid}
head(northatlantic_votes_raw$afstemningid)
```


#### northatlantic_votes_raw$aktørid

...

```{r northatlantic_votes_raw-aktørid}
head(northatlantic_votes_raw$aktørid)
```


#### northatlantic_votes_raw$opdateringsdato

...

```{r northatlantic_votes_raw-opdateringsdato}
head(northatlantic_votes_raw$opdateringsdato)
```

------------------------------------------------------------------------

### ballot_results_ft

After all ballots are downloaded, they are processed and then stored in this file. As of `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`, `ballot_results_ft.rds` contains `r nrow(ballot_results_ft)` observations of `r ncol(ballot_results_ft)` variables.

`ballot_results_ft` is provided as `rds` file in `/data/processed/`. The unprocessed [raw data](#ballot_info_raw) is available as `rds` file in `/data/raw/`.

```{r ballot_results_ft-intro}
str(ballot_results_ft)
```

Descriptions of all variables in `ballot_results_ft` are provided in the following sections.

#### ballot_results_ft$ballot_id

...

```{r ballot_results_ft-ballot_id}
head(ballot_results_ft$ballot_id)
```

#### ballot_results_ft$meeting_id

...

```{r ballot_results_ft-meeting_id}
head(ballot_results_ft$meeting_id)
```

#### ballot_results_ft$ballot_pass

...

```{r ballot_results_ft-ballot_pass}
summary(ballot_results_ft$ballot_pass)
```

#### ballot_results_ft$ballot_date

...

```{r ballot_results_ft-ballot_date}
head(ballot_results_ft$ballot_date)
```

#### ballot_results_ft$ft_topic

...

```{r ballot_results_ft-ft_topic}
head(ballot_results_ft$ft_topic)
```

#### ballot_results_ft$ft_for

...

```{r ballot_results_ft-ft_for}
summary(ballot_results_ft$ft_for)
```

#### ballot_results_ft$ft_against

...

```{r ballot_results_ft-ft_against}
summary(ballot_results_ft$ft_against)
```

#### ballot_results_ft$ft_abstention

...

```{r ballot_results_ft-ft_abstention}
summary(ballot_results_ft$ft_abstention)
```

#### ballot_results_ft$ft_absent

...

```{r ballot_results_ft-ft_absent}
summary(ballot_results_ft$ft_absent)
```

#### ballot_results_ft$ft_process_id

...

```{r ballot_results_ft-ft_process_id}
head(ballot_results_ft$ft_process_id)
```

#### ballot_results_ft$ft_process_step

...

```{r ballot_results_ft-ft_process_step}
head(ballot_results_ft$ft_process_step)
```

#### ballot_results_ft$ballot_nr

...

```{r ballot_results_ft-ballot_nr}
head(ballot_results_ft$ballot_nr)
```

#### ballot_results_ft$ballot_type_id

...

```{r ballot_results_ft-ballot_type_id}
table(ballot_results_ft$ballot_type_id)
```

#### ballot_results_ft$comment

...

```{r ballot_results_ft-comment}
head(ballot_results_ft$comment)
```

#### ballot_results_ft$ballot_result_string

...

```{r ballot_results_ft-ballot_result_string}
head(ballot_results_ft$ballot_result_string)
```

------------------------------------------------------------------------

### ballot_info_raw {#ballot_info_raw}

`ballot_info_raw` contains the downloaded data on voting records before any preprocessing. As per `r format(file.info(here("data", "raw", "ballot_info_raw.rds"))$mtime, "%B %Y")`, `ballot_info_raw.rds` contains `r nrow(ballot_info_raw)` observations of `r ncol(ballot_info_raw)` variables.

`ballot_info_raw` is provided as `rds` file in `/data/raw/`. The processed [data](#ballot_results_ft) is available as `rds` file in `/data/processed`.

```{r}
str(ballot_info_raw)
```

Descriptions of all variables in `ballot_info_raw` are provided in the following sections.

#### ballot_info_raw$id

...

```{r}
head(ballot_info_raw$id)
```

#### ballot_info_raw$nummer

...

```{r}
head(ballot_info_raw$nummer)
```

#### ballot_info_raw$konklusion

...

```{r}
head(ballot_info_raw$konklusion)
```

#### ballot_info_raw$vedtaget

...

```{r}
summary(ballot_info_raw$vedtaget)
```

#### ballot_info_raw$kommentar

...

```{r}
head(ballot_info_raw$kommentar)
```

#### ballot_info_raw$mødeid

...

```{r}
head(ballot_info_raw$mødeid)
```

#### ballot_info_raw$typeid

...

```{r}
table(ballot_info_raw$typeid)
```

#### ballot_info_raw$sagstrinid

...

```{r}
head(ballot_info_raw$sagstrinid)
```

#### ballot_info_raw$sagstrin_titel

...

```{r}
head(ballot_info_raw$sagstrin_titel)
```

#### ballot_info_raw$sag_titel

...

```{r}
head(ballot_info_raw$sag_titel)
```

#### ballot_info_raw$dato

...

```{r}
head(ballot_info_raw$dato)
```

#### ballot_info_raw$opdateringsdato

...

```{r}
head(ballot_info_raw$opdateringsdato)
```

------------------------------------------------------------------------

### cabinets_fo {#cabinets_fo}

The dataset contains information on the coalition governments of the Faroe Islands (Landsstýri), in particular a timeline including the parties that are part of each cabinet. As per `r format(file.info(here("data", "processed", "csv", "cabinets_fo.csv"))$mtime, "%B %Y")`, `cabinets_fo` contains information on `r nrow(cabinets_fo)` cabinets stored in `r ncol(cabinets_fo)` variables. This data set spans the timeframe covered by the voting database -- from `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")` until the most recent update of this data set on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`.

`cabinets_fo` is provided as `rds` file in `/data/processed` and `csv` file in `/data/processed/csv`. Metadata for the `csv` file is provided in an accompanying `json` metadata file. 

See also [cabinets_gl](#cabinets_gl) and [cabinets_dk](#cabinets_dk).

```{r cabinets_fo-intro}
str(cabinets_fo)
```

Descriptions of all variables in `cabinets_fo` are provided in the following sections.

#### cabinets_fo$cabinet

Each cabinet formed in the Faroe Islands (Landsstýri) is assigned a human-readable identifier. The cabinets are usually named after the head of government, using their surname(s), followed by an integer number for multiple cabinets headed by the same person. Because in the timeframe covered by this data set, there have been two Faroese governments with a PM named Johannesen, the first letter of their first name is also appended to the `cabinet` variable. This variable is stored as value of the type `r typeof(cabinets_fo$cabinet)` as `r class(cabinets_fo$cabinet)` variable.

```{r cabinets_fo-cabinet}
head(cabinets_fo$cabinet)
```

#### cabinets_fo$wikidata_id

The `wikidata_id` variable stores the `QID` linking to the Wikidata entity representing the cabinet in question, making it easy to retrieve additional information from Wikidata, if necessary. This variable is stored as value of the type `r typeof(cabinets_fo$wikidata_id)` as `r class(cabinets_fo$wikidata_id)` variable.

```{r cabinets_fo-wikidata_id}
head(cabinets_fo$wikidata_id)
```

#### cabinets_fo$location

`location` indicates where a cabinet is formed -- in the Faroe Islands (`FO`). This variable is stored as value of the type `r typeof(cabinets_fo$location)` as `r class(cabinets_fo$location)` variable. When merging data, this proved to be helpful to distinguish between the different political parties, some of which share a common abbreviation across regions.

```{r cabinets_fo-location}
table(cabinets_fo$location)
```

#### cabinets_fo$start

The date on which each cabinet is formed is stored as `r class(cabinets_fo$start)` variable of the type `r typeof(cabinets_fo$start)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_fo$start), "%B %d, %Y")` (`r min(cabinets_fo$start)`) and the most recent entry from `r format(max(cabinets_fo$start), "%B %d, %Y")` (`r max(cabinets_fo$start)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_fo.csv"))$mtime, "%B %Y")`.

```{r cabinets_fo-start}
head(cabinets_fo$start)
```

#### cabinets_fo$end

The date on which each cabinet is succeeded by the next one is stored as `r class(cabinets_fo$end)` variable of the type `r typeof(cabinets_fo$end)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_fo$end), "%B %d, %Y")` (`r min(cabinets_fo$end)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_fo.csv"))$mtime, "%B %Y")`.

Note that this date does not necessarily correspond to the date when a government 'collapses' or officially announces its resignation. Rather, the date denotes the day of the transition of power to the next cabinet.

```{r cabinets_fo-end}
head(cabinets_fo$end)
```

#### cabinets_fo$FO_A

`FO_A` indicates whether the Faroese political party **Fólkaflokkurin** (`A`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_A)` as `r class(cabinets_fo$FO_A)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_A` which only stores statements on official cabinet membership.

```{r cabinets_fo-FO_A}
summary(cabinets_fo$FO_A)
```

#### cabinets_fo$FO_B

`FO_B` indicates whether the Faroese political party **Sambandsflokkurin** (`B`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_B)` as `r class(cabinets_fo$FO_B)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_B` which only stores statements on official cabinet membership.

```{r cabinets_fo-FO_B}
summary(cabinets_fo$FO_B)
```

#### cabinets_fo$FO_C

`FO_C` indicates whether the Faroese political party **Javnaðarflokkurin** (`C`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_C)` as `r class(cabinets_fo$FO_C)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_C` which only stores statements on official cabinet membership.

```{r cabinets_fo-FO_C}
summary(cabinets_fo$FO_C)
```

#### cabinets_fo$FO_D

`FO_D` indicates whether the Faroese political party **Sjálvstýri** (`D`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_D)` as `r class(cabinets_fo$FO_D)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_D` which only stores statements on official cabinet membership.

```{r cabinets_fo-FO_D}
summary(cabinets_fo$FO_D)
```

#### cabinets_fo$FO_E

`FO_E` indicates whether the Faroese political party **Tjóðveldi** (`E`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_E)` as `r class(cabinets_fo$FO_E)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_E` which only stores statements on official cabinet membership.

```{r cabinets_fo-FO_E}
summary(cabinets_fo$FO_E)
```

#### cabinets_fo$FO_F

`FO_F` indicates whether the Faroese political party **Framsókn** (`F`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_F)` as `r class(cabinets_fo$FO_F)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_F` which only stores statements on official cabinet membership.

```{r cabinets_fo-FO_F}
summary(cabinets_fo$FO_F)
```

#### cabinets_fo$FO_H

`FO_H` indicates whether the Faroese political party **Miðflokkurin** (`H`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_H)` as `r class(cabinets_fo$FO_H)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_H` which only stores statements on official cabinet membership.

```{r cabinets_fo-FO_H}
summary(cabinets_fo$FO_H)
```

------------------------------------------------------------------------

### cabinets_gl {#cabinets_gl}

The dataset contains information on the coalition governments of Greenland (Naalakersuisut), in particular a timeline including the parties that are part of each cabinet. As per `r format(file.info(here("data", "processed", "csv", "cabinets_gl.csv"))$mtime, "%B %Y")`, `cabinets_gl` contains information on `r nrow(cabinets_gl)` cabinets stored in `r ncol(cabinets_gl)` variables. This data set spans the timeframe covered by the voting database -- from `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")` until the most recent update of this data set on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`.

`cabinets_gl` is provided as `rds` file in `/data/processed` and `csv` file in `/data/processed/csv`. Metadata for the `csv` file is provided in an accompanying `json` metadata file. 

See also [cabinets_fo](#cabinets_fo) and [cabinets_dk](#cabinets_dk).

```{r cabinets_gl-intro}
str(cabinets_gl)
```

Descriptions of all variables in `cabinets_gl` are provided in the following sections.
