---
title: Codebook
authors:
  - name: Moritz Twente
    affiliation: University of Basel
    email: moritz.twente@unibas.ch
    orcid: 0009-0005-7187-9774
date-modified: last-modified
bibliography: ../assets/nordatlantisk-ft.bib
link-citations: true
lang: en
---

```{r setup}
#| echo: false
#| message: false

# Setup -----
## Packages -----

library(here)
library(ggplot2)
library(dplyr)
library(readr)
library(knitr)
library(forcats)
library(lubridate)

## Read Data -----

### List of MPs -----
mp_names <- readRDS(here("data", "processed", "MP_names.rds"))

### List of political parties -----
political_parties <- read.csv(here("data", "static", "political_parties.csv"), sep = ";", check.names = FALSE)

### Voting Records Database -----
northatlantic_votes <- readRDS(here("data", "processed", "northatlantic_votes.rds"))
northatlantic_votes_raw <- read.csv(here("data", "raw", "northatlantic_votes_raw.csv"), check.names = FALSE)
ballot_info_raw <- read.csv(here("data", "raw", "ballot_info_raw.csv"), check.names = FALSE)
ballot_results_ft <- readRDS(here("data", "processed", "ballot_results_ft.rds"))
ballot_topics_raw <- read.csv(here("data", "raw", "ballot_topics_raw.csv"), check.names = FALSE)

northatlantic_ft <- readRDS(here("data", "processed", "northatlantic_ft.rds"))

plot_dataset <- northatlantic_ft %>%
  left_join(mp_names %>% select(MP_id, origin), by = "MP_id")

### Timeline of Mandates and Cabinets -----
mandates <- read.delim(here("data", "static", "MP_dates.csv"), sep = ";", stringsAsFactors = FALSE)
elections <- read.delim(here("data", "static", "election_dates.csv"), sep = ";", stringsAsFactors = FALSE)
cabinets_dk <- readRDS(here("data", "processed", "cabinets_dk.rds"))

cabinets_fo <- readRDS(here("data", "processed", "cabinets_fo.rds"))
cabinets_gl <- readRDS(here("data", "processed", "cabinets_gl.rds"))
cabinets_fo_gl <- full_join(cabinets_gl, cabinets_fo)

#### Convert dates
mandates <- mandates %>%
  mutate(
    start = ymd(start),
    end   = ymd(end),
    # Replace NA in "end" with today's date
    end   = if_else(is.na(end), Sys.Date(), end)
  )

cabinets_fo <- cabinets_fo %>%
    mutate(
      start = ymd(start),
      end   = ymd(end),
      end   = coalesce(end, Sys.Date())
    )

cabinets_gl <- cabinets_gl %>%
    mutate(
      start = ymd(start),
      end   = ymd(end),
      end   = coalesce(end, Sys.Date())
    )

cabinets_dk <- cabinets_dk %>%
    mutate(
      start = ymd(start),
      end   = ymd(end),
      end   = coalesce(end, Sys.Date())
    )

## Manipulate Data -----

### Avoid confusing MPs with the same last name
mandates <- mandates %>%
  mutate(
    plotting_name = case_when(
      MP_id == "12283" ~ "A. V. Johannesen",
      MP_id == "6687"  ~ "K. L. Johannesen",
      TRUE             ~ surname
    )
  )

plot_dataset <- plot_dataset %>%
  mutate(
    plotting_name = case_when(
      MP_id == "12283" ~ "A. V. Johannesen",
      MP_id == "6687"  ~ "K. L. Johannesen",
      TRUE             ~ surname
    )
  )

### Order dataset by MP surnames for plotting
plot_dataset_ordered <- plot_dataset %>%
  mutate(surname = fct_reorder(surname, vote_type_id, .fun = length)) %>%
  mutate(plotting_name = fct_reorder(plotting_name, vote_type_id, .fun = length)) %>%
  mutate(vote_type_id = fct_relevel(vote_type_id, "1", "2", "4", "3"))

### Subset only with votes that were actually cast
plot_dataset_without_absences <- subset(plot_dataset_ordered, vote_type_id != 3) %>%
  mutate(surname = fct_reorder(surname, vote_type_id, .fun = length)) %>%
  mutate(plotting_name = fct_reorder(plotting_name, vote_type_id, .fun = length))

## Set Plotting Theme -----

theme_nordatlantisk_basis <- function(){
  
  theme_grey() %+replace%
    theme(axis.title = element_blank(),
          axis.ticks.y = element_blank(),
          panel.background = element_blank(),
          panel.grid.major.x = element_line(color = "#000000", linewidth = 0.1),
          panel.grid.minor.x = element_line(color = "#000000", linewidth = 0.1),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.y = element_blank(),
          axis.ticks.x = element_line(color = "#000000", linewidth = 0.1),
          axis.line.y.left = element_line(color = "#000000", linewidth = 0.1))
}

```

## Introduction {#introduction}

This codebook provides descriptions of the `nordatlantisk-ft` data set, i.e. of all files in `/data/`. Variables are described for each file individually with information on connections to other variables within the pipeline to create the data set. All data, unless otherwise specified, is retrieved from the records of the parliament of Denmark, @folketingetFolketingetsAbneData2025.

All data is available in `rds` format that can be read in an R Session via `readRDS()`. Where data is also available in `csv` format, the tabular metadata is provided in `json` files at `/data/processed/csv` according to the W3C Metadata Vocabulary for Tabular Data [@w3cW3CRecommendationMetadata2015].

## File and Variable Descriptions {#file-and-variable-descriptions}

The general structure of the data used in the workflow to compile the final `northatlantisk_ft.csv` output is illustrated in @fig-datamodel.

```{mermaid datamodel}
%%| label: fig-datamodel
%%| fig-cap: Chart illustrating the files used to create the dataset including variable names and types. Click on an element to jump to its description in the codebook.

classDiagram
    direction LR

    MP_dates -- MP_names
    MP_dates .. election_dates
    MP_dates .. political_parties

    MP_names *-- northatlantic_ft

    northatlantic_votes <|-- northatlantic_ft
    ballot_results_ft <|-- northatlantic_ft
    ballot_topics_raw <|-- northatlantic_ft

    MP_names *-- northatlantic_votes_raw
    northatlantic_votes_raw <|-- northatlantic_votes

    ballot_info_raw <|-- ballot_results_ft

    cabinets_fo .. cabinets_gl
    cabinets_gl .. cabinets_dk
    cabinets_dk <|-- northatlantic_ft

    class northatlantic_ft {
        ballot_id : int
        MP_id : int
        surname : string
        origin: string
        party : string
        gvt_party_at_home: bool
        vote_type_id : int
        ballot_pass : bool
        ft_process_step : string
        ft_topic_id : int
        ft_topic : string
        ft_for : int
        ft_against : int
        ft_abstention : int
        ft_absent : int
        ballot_date : date
        ballot_type_id : int
        gvt_type_dk : string
        gvt_bloc_dk : string
        comment : string
        ballot_result_string : int
    }

        class northatlantic_votes {
        vote_id : int
        vote_type_id : int
        ballot_id : int
        MP_id : int
    }

        class MP_dates {
        surname : string
        firstname : string
        MP_id: int
        origin: string
        party : string
        start : date
        end : date
        substitute : bool
    }

    class election_dates {
        election : string
        date : date
    }

    class MP_names {
        surname : string
        first_name : string
        MP_id : int
        wikidata_id : string
        origin : string
        party : string
        substitute : bool
    }

    class ballot_results_ft {
        ballot_id : int
        meeting_id : int
        ballot_pass : bool
        ballot_date : date
        ft_for : int
        ft_against : int
        ft_abstention : int
        ft_absent : int
        ft_process_id : int
        ballot_nr : int
        ballot_type_id : int
        comment : string
        ballot_result_string : string
    }

    class ballot_info_raw {
        id : int
        nummer : int
        konklusion : string
        vedtaget : bool
        kommentar : string
        mødeid : int
        typeid : int
        sagstrinid : int
        opdateringsdato : date
    }

    class ballot_topics_raw {
        ft_process_id : int
        ft_process_step : string
        ft_topic_id : int
        ft_topic : string
    }

    class northatlantic_votes_raw {
        id : int
        typeid : int
        afstemningid : int
        aktørid : int
        opdateringsdato : date
    }

    class political_parties {
        party : string
        full_name : string
        wikidata_id : string
        party_family : string
        colour : string
        origin : string
        left_right : float
        state_market : float
        liberty_authority : float
        anti_pro_eu : float
    }

    class cabinets_fo {
      cabinet: string
      wikidata_id: string
      location: string
      start: date
      end: date
      FO_&ast;: bool
    }

    class cabinets_gl {
      cabinet: string
      wikidata_id: string
      location: string
      start: date
      end: date
      GL_&ast;: bool
    }

    class cabinets_dk {
      cabinet: string
      wikidata_id: string
      bloc: string
      type: string
      start: date
      end: date
      DK_&ast;: bool
    }

style ballot_info_raw fill:#D1BBD7
style ballot_results_ft fill:#D1BBD7

style ballot_topics_raw fill:#253C78,color:#FFFFFF

style northatlantic_ft fill:#F7CB45

style northatlantic_votes_raw fill:#FFEAAE
style northatlantic_votes fill:#FFEAAE

style MP_names fill:#6195CF,color:#FFFFFF
style MP_dates fill:#6195CF,color:#FFFFFF

%% not implemented %% click MP_dates href "#mp_dates" "tooltip"
click MP_names href "#mp_names" "tooltip"
click northatlantic_votes_raw href "#northatlantic_votes_raw" "tooltip"
click northatlantic_votes href "#northatlantic_votes" "tooltip"
click ballot_info_raw href "#ballot_info_raw" "tooltip"
click ballot_results_ft href "#ballot_results_ft" "tooltip"
click ballot_topics_raw href "#ballot_topics_raw" "tooltip"
click cabinets_fo href "#cabinets_fo" "tooltip"
click cabinets_gl href "#cabinets_gl" "tooltip"
click cabinets_dk href "#cabinets_dk" "tooltip"
click northatlantic_ft href "#northatlantic_ft" "tooltip"
```

### MP_names {#mp_names}

`MP_names` is provided in `csv` and `rds` formats in `/data/processed`. The `csv` file serves as starting point for building the data set, as the workflow pipeline[^1] retrieves data from [Folketingets Open Data Portal](https://oda.ft.dk) based on which MPs are listed in this file. This repository is shipped with a list of all Folketinget MPs that have represented the Faroe Islands and Greenland from `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")` until the last update of this data set (on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`), which results in `r nrow(mp_names)` MPs.

[^1]: See [README](/index.qmd) or [`_targets.R`](/_targets.R)

```{r}
head(mp_names)
```

Descriptions of all variables in `MP_names` are provided in the following sections. The only variable necessary to execute the workflow is stored as [`MP_names$MP_id`](#mp_namesmp_id).

#### MP_names\$surname {#mp_namessurname}

All surname(s) are stored as values of the type `r typeof(mp_names$surname)`. Names are spelled according to standardised orthography and, in terms of morphology, in nominative (Faroese) resp. absolutive (Greenlandic) case. Because there are be multiple MPs with the same surname(s), refer to [`MP_names$MP_id`](#mp_namesmp_id) instead for reliable identification.

This column is not necessary for successfully executing the workflow pipeline, but it is used to map MP names to the corresponding IDs for increased readability of resulting plots.

```{r}
head(mp_names$surname)
```

#### MP_names\$first_name

All first names are stored as values of the type `r typeof(mp_names$first_name)`. Names are spelled according to standardised orthography and, morphologically, in nominative (Faroese) resp. absolutive (Greenlandic) case. Because there may be multiple MPs with the same first name(s), refer to [`MP_names$MP_id`](#MP_names_MP_id) instead for reliable identification.

This column is not necessary for successfully executing the workflow pipeline, but it can be used to map MPs’ names to the corresponding IDs for increased readability of resulting plots.

```{r}
head(mp_names$first_name)
```

#### MP_names\$MP_id {#mp_namesmp_id}

Each MP is assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each `MP_id` thus is a unique identifier for one member of Folketinget. All IDs are stored as values of the type `r typeof(mp_names$MP_id)` as `r class(mp_names$MP_id)` variable. It is possible to use these IDs e.g. for querying the [the online database](https://oda.ft.dk) to retrieve documents that relate to a given MP or to find out which parliamentary processes this MP has been engaged in. The Folketing ID is also available as Wikidata Property [P10207](https://www.wikidata.org/wiki/Property:P10207).

`MP_id` is the only necessary column in `MP_names` for successfully executing the workflow pipeline.

```{r}
head(mp_names$MP_id)
```

This variable corresponds to the `aktørid` variable and the `Aktør` resource in [the Folketing online database](https://oda.ft.dk). Note that in Folketinget’s data model, ministries, parliamentary commissions, NGOs etc. are also listed as `Aktør` with their resp. `aktørid`.

#### MP_names\$wikidata_id {#mp_nameswikidata_id}

Apart from [`MP_names$MP_id`](#MP_names_MP_id), each MP's Wikidata QID is stored in `MP_names` for further processing options. This identifier can be used to query Wikidata to supplement the dataset with further information. At the moment, this identifier is not used in any step of the processing pipeline.

```{r}
head(mp_names$wikidata_id)
```

#### MP_names\$origin {#mp_namesorigin}

`origin` indicates whether an MP was elected in either Greenland (`GL`) or the Faroe Islands (`FO`). This variable is stored as value of the type `r typeof(mp_names$origin)` as `r class(mp_names$origin)` variable. Note that this only indicates where the MP in question ran for office. MPs with ties to Greenland or the Faroe Islands who won a Folketinget mandate in a continental election district are thus not part of this data set, as they are not considered *Northatlantic* MPs.

```{r}
summary(mp_names$origin)
```

#### MP_names\$party {#mp_namesparty}

The political party that each MP belongs to is stored as value of the type `r typeof(mp_names$party)` as `r class(mp_names$party)` variable. As per January 2024, there have been two MPs from Greenland who left their party – Siumut, in both cases – during their time in office and joined other parties. For now, the `MP_names` data frame does not include information on membership periods etc. At the moment, these two cases are therefore stored with a single string without distinguishing between membership periods.

```{r}
summary(mp_names$party)
```

All represented political parties are listed in @tbl-parties with additional information (where available) on their positions from the ParlGov dataset [@doringParlGov2022Release2022].

Since 2004, MPs from the Faroe Islands were members of `r sum(political_parties$origin == "FO")` different political parties. Voters in Greenland elected politicians from `r sum(political_parties$origin == "GL") - 2` different political parties. However, two of the Greenlandic representatives -- Aleqa Hammond and Aki-Matilda Høegh-Dam -- switched party affiliation during their time as member of Folketinget and became members of newly formed parties (Nunatta Qitornai and Naleraq[^2]).

[^2]: Both parties have been formed quite recently. See @ahlnessNunattaQitornaiParty2020 for general information on Nunatta Qitornai and their policies. Nunatta Qitornai has de facto been dissolved after the 2021 Inatsisartut election [@hviidVittusQujaukitsoqMelder2025].

```{r parties-list}
#| echo: false
#| message: false
#| label: tbl-parties
#| tbl-cap: List of political parties from Greenland and the Faroe Islands with a MP in Folketinget since 2004.

political_parties <- political_parties |>
  mutate(
    full_name_linked = ifelse(
      is.na(wikidata_id) | wikidata_id == "",
      full_name,
      paste0("[", full_name, "](https://wikidata.org/wiki/", wikidata_id, ")")
    )
  )

parties_gl <- political_parties |>
  filter(origin == "GL") |>
  select(party, full_name_linked, party_family,
         left_right, state_market, liberty_authority, anti_pro_eu)

parties_fo <- political_parties |>
  filter(origin == "FO") |>
  select(party, full_name_linked, party_family,
         left_right, state_market, liberty_authority, anti_pro_eu)

printable_names <- c(
  "Party", "Full Name", "Party Family",
  "Left–Right", "State–Market", "Liberty–Authority", "Anti–Pro-EU"
)

kable(
  parties_gl,
  caption = "Greenlandic Parties",
  col.names = printable_names,
  escape = FALSE
)

kable(
  parties_fo,
  caption = "Faroese Parties",
  col.names = printable_names,
  escape = FALSE)
```

#### MP_names\$substitute

Some of the politicians that are part of this data set joined Folketinget in the role of a substitute member, filling in for the originally elected MPs while they were on leave [cf. @harderFaeroskeOgGronlandske2022, 12-13]. Doris Jakobsen (SIU), Lisbeth Petersen (B), Magni Arge (E) and Sjúrður Skaale (C) all first became MPs as substitute members, but later joined as regular MPs after a general election. For now, they are listed as full members in this dataset. Data on membership periods is available in [`/data/static/MP_dates.csv`](/data/static/MP_dates.csv).

```{r}
summary(mp_names$substitute)
```

------------------------------------------------------------------------

### northatlantic_votes {#northatlantic_votes}

`northatlantic_votes` is provided as `rds` file in `/data/processed/`. After all votes cast by the MPs specified in [`MP_names`](#mp_names) are downloaded, they are processed and then stored in this file. The unprocessed [raw data](#northatlantic_votes_raw) is available as `csv` file in `/data/raw/`. As per `r format(file.info(here("data", "processed", "northatlantic_votes.rds"))$mtime, "%B %Y")`, `northatlantic_votes.rds` contains `r nrow(northatlantic_votes)` observations of `r ncol(northatlantic_votes)` variables.

```{r}
head(northatlantic_votes)
```

Descriptions of all variables in `northatlantic_votes` are provided in the following sections.

#### northatlantic_votes\$vote_id {#northatlantic_votesvote_id}

All votes cast in Folketinget are assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each vote ID is thus a unique identifier for one vote cast in Folketinget. All IDs are stored as values of the type `r typeof(northatlantic_votes$vote_id)` as `r class(northatlantic_votes$vote_id)` variable.

This variable corresponds to the `id` variable and the `Stemme` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
head(northatlantic_votes$vote_id)
```

#### northatlantic_votes\$vote_type_id {#northatlantic_votesvote_type_id}

All votes cast in Folketinget are recorded using numeric values that correspond to the MP’s decision (see @tbl-typeid). All Vote Type IDs are stored as values of the type `r typeof(northatlantic_votes$vote_type_id)` as `r class(northatlantic_votes$vote_type_id)` variable.

| ID | Result | English | n |
|:-----------------|:------------------|:-----------------|-----------------:|
| 1 | for | for | `r length(northatlantic_votes$vote_type_id[northatlantic_votes$vote_type_id == "1"])` |
| 2 | imod | against | `r length(northatlantic_votes$vote_type_id[northatlantic_votes$vote_type_id == "2"])` |
| 3 | fravær | absence | `r length(northatlantic_votes$vote_type_id[northatlantic_votes$vote_type_id == "3"])` |
| 4 | hverken for eller imod | abstention | `r length(northatlantic_votes$vote_type_id[northatlantic_votes$vote_type_id == "4"])` |

: Vote Type IDs as used by Folketingets Open Data Service {#tbl-typeid} {.striped .hover}

This variable corresponds to the `typeid` variable and the `Stemmetype` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
head(northatlantic_votes$vote_type_id)
```

#### northatlantic_votes\$ballot_id {#northatlantic_votesballot_id}

All ballot procedures in Folketinget are assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each ballot ID is thus a unique identifier for one ballot in Folketinget. All IDs are stored as values of the type `r typeof(northatlantic_votes$ballot_id)` as `r class(northatlantic_votes$ballot_id)` variable.

This variable corresponds to the [`ballot_results_ft$ballot_id`](#ballot_results_ftballot_id) variable and the `Afstemning` resource in [the Folketing online database](https://oda.ft.dk). Take care not to confuse `ballot_id` with [`ballot_results_ft$ballot_nr`](#ballot_results_ftballot_nr).

```{r}
head(northatlantic_votes$ballot_id)
```

#### northatlantic_votes\$MP_id {#northatlantic_votesmp_id}

See [`MP_names$MP_id`](#mp_namesmp_id).

```{r}
head(northatlantic_votes$MP_id)
```

------------------------------------------------------------------------

### northatlantic_votes_raw {#northatlantic_votes_raw}

`northatlantic_votes_raw` is provided as `csv` file in `/data/raw/`. It contains the downloaded data on voting records before any preprocessing. The [processed data](#northatlantic_votes) is available as `rds` file in `/data/processed`. As of `r format(file.info(here("data", "raw", "northatlantic_votes_raw.csv"))$mtime, "%B %Y")`, `northatlantic_votes_raw.csv` contains `r nrow(northatlantic_votes_raw)` observations of `r ncol(northatlantic_votes_raw)` variables.

```{r}
head(northatlantic_votes_raw)
```

Descriptions of all variables in `northatlantic_votes_raw` are provided in the following sections.

#### northatlantic_votes_raw\$id

See [`northatlantic_votes$vote_id`](#northatlantic_votesvote_id). In the raw data, `id` is stored as `r typeof(northatlantic_votes_raw$id)` value.

```{r}
head(northatlantic_votes_raw$id)
```

#### northatlantic_votes_raw\$typeid

See [`northatlantic_votes$vote_type_id`](#northatlantic_votesvote_type_id). In the raw data, `typeid` is stored as `r typeof(northatlantic_votes_raw$typeid)` value.

```{r}
head(northatlantic_votes_raw$typeid)
```

#### northatlantic_votes_raw\$afstemningid

See [`northatlantic_votes$ballot_id`](#northatlantic_votesballot_id). In the raw data, `afstemningid` is stored as `r typeof(northatlantic_votes_raw$afstemningid)` value.

Take care not to confuse `afstemningid` with [`ballot_results_ft$ballot_nr`](#ballot_results_ftballot_nr).

```{r}
head(northatlantic_votes_raw$afstemningid)
```

#### northatlantic_votes_raw\$aktørid

See [`northatlantic_votes$MP_id`](#northatlantic_votesmp_id). In the raw data, `aktørid` is stored as `r typeof(northatlantic_votes_raw$aktørid)` value.

```{r}
head(northatlantic_votes_raw$aktørid)
```

#### northatlantic_votes_raw\$opdateringsdato

For all records kept in [the Folketing online database](https://oda.ft.dk), the time stamp of its last update is stored in `opdateringsdato`. All dates are stored as values of the type `r typeof(northatlantic_votes_raw$opdateringsdato)`. The time stamps are formatted as `%Y-%m-%dT%T`, with some values even at split second level.

This variable is eliminated from [`northatlantic_votes`](#northatlantic_votes) as a result of data processing.

```{r}
head(northatlantic_votes_raw$opdateringsdato)
```

------------------------------------------------------------------------

### ballot_results_ft {#ballot_results_ft}

`ballot_results_ft` is provided as `rds` file in `/data/processed/`. After all ballots are downloaded, they are processed and then stored in this file. The unprocessed [raw data](#ballot_info_raw) is available as `csv` file in `/data/raw/`. As of `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`, `ballot_results_ft.rds` contains `r nrow(ballot_results_ft)` observations of `r ncol(ballot_results_ft)` variables.

```{r}
str(ballot_results_ft)
```

Descriptions of all variables in `ballot_results_ft` are provided in the following sections.

#### ballot_results_ft\$ballot_id {#ballot_results_ftballot_id}

See [northatlantic_votes\$ballot_id](#northatlantic_votesballot_id). Take care not to confuse `ballot_id` with [`ballot_nr`](#ballot_results_ftballot_nr).

```{r}
head(ballot_results_ft$ballot_id)
```

#### ballot_results_ft\$meeting_id {#ballot_results_ftmeeting_id}

All meetings in Folketinget are assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each meeting ID is thus a unique identifier for one meeting in Folketinget. All IDs are stored as values of the type `r typeof(ballot_results_ft$meeting_id)` as `r class(ballot_results_ft$meeting_id)` variable.

This variable corresponds to the [`mødeid`](#ballot_info_rawmødeid) variable and the `Møde` resource in [the Folketing online database](https://oda.ft.dk).

This variable is eliminated when joining `ballot_results_ft` and `northatlantic_votes` to [`northatlantic_ft`](#northatlantic_ft).

```{r}
head(ballot_results_ft$meeting_id)
```

#### ballot_results_ft\$ballot_pass {#ballot_results_ftballot_pass}

The result of all ballots in Folketinget is stored in `ballot_pass` as `r typeof(ballot_results_ft$ballot_pass)` variable. If parliament votes in favor of a proposal, it passes and `ballot_pass` is assigned `TRUE`; if parliament votes a proposal down, it does not pass and `ballot_pass` is assigned `FALSE`.

This variable corresponds to the [`vedtaget`](#ballot_info_rawvedtaget) variable in the `Afstemning` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
head(ballot_results_ft$ballot_pass)
```

#### ballot_results_ft\$ballot_date {#ballot_results_ftballot_date}

The date on which each ballot takes place in Folketinget is stored as `r class(ballot_results_ft$ballot_date)` variable of the type `r typeof(ballot_results_ft$ballot_date)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(ballot_results_ft$ballot_date), "%B %d, %Y")` (`r min(ballot_results_ft$ballot_date)`) and the most recent entry from `r format(max(ballot_results_ft$ballot_date), "%B %d, %Y")` (`r max(ballot_results_ft$ballot_date)`) as of `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`.

This variable is added to the data using the [`get_meeting_dates()`](/src/targets/get_meeting_dates.R) function.

```{r}
head(ballot_results_ft$ballot_date)
```

#### ballot_results_ft\$ft_for {#ballot_results_ftft_for}

In `ft_for`, the number of votes cast in favor of a proposal is stored as `r class(ballot_results_ft$ft_for)` variable of the type `r typeof(ballot_results_ft$ft_for)`. Since the record keeping of Folketinget is inconsistent regarding the coding of ballot results, values for this variable are calculated in two steps. First, using the retrieved raw data, [`get_missing_info()`](/src/targets/get_missing_info.R) sums up all recorded individual votes in favor of the proposal using the `switch()` function on every row where [`ballot_info_raw$typeid`](#ballot_info_rawtypeid) equals `1`. The results of a considerable share of ballots are recorded only using [a – Danish – character string](#ballot_results_ftcomment) instead of in a list of votes. In these cases, the number of votes in favor of those proposals is extracted with [`clean_ballot_results()`](/src/targets/clean_ballot_results.R) using the `strex` package and then added to the number of approving votes from the first step.

The maximum value stored in `ft_for` is `r max(ballot_results_ft$ft_for, na.rm = TRUE)` and the minimum value stored in `ft_for` is `r min(ballot_results_ft$ft_for, na.rm = TRUE)`. As the total number of MPs in Folketinget is 179, the value of `ft_for` cannot be greater than `179`.

```{r}
head(ballot_results_ft$ft_for)
```

#### ballot_results_ft\$ft_against {#ballot_results_ftft_against}

In `ft_against`, the number of votes cast against a proposal is stored as `r class(ballot_results_ft$ft_against)` variable of the type `r typeof(ballot_results_ft$ft_against)`. Since the record keeping of Folketinget is inconsistent regarding the coding of ballot results, values for this variable are calculated in two steps. First, using the retrieved raw data, [`get_missing_info()`](/src/targets/get_missing_info.R) sums up all recorded individual votes in favor of the proposal using the `switch()` function on every row where [`ballot_info_raw$typeid`](#ballot_info_rawtypeid) equals `2`. The results of a considerable share of ballots are recorded only using [a – Danish – character string](#comment) instead of in a list of votes. In these cases, the number of no-votes is extracted with [`clean_ballot_results()`](/src/targets/clean_ballot_results.R) using the `strex` package and then added to the number of no-votes from the first step.

The maximum value stored in `ft_against` is `r max(ballot_results_ft$ft_against, na.rm = TRUE)` and the minimum value stored in `ft_against` is `r min(ballot_results_ft$ft_against, na.rm = TRUE)`. As the total number of MPs in Folketinget is 179, the value of `ft_against` cannot be greater than `179`.

```{r}
head(ballot_results_ft$ft_against)
```

#### ballot_results_ft\$ft_abstention {#ballot_results_ftft_abstention}

In `ft_abstention`, the number of abstaining votes is stored as `r class(ballot_results_ft$ft_abstention)` variable of the type `r typeof(ballot_results_ft$ft_abstention)`. Since the record keeping of Folketinget is inconsistent regarding the coding of ballot results, values for this variable are calculated in two steps. First, using the retrieved raw data, [`get_missing_info()`](/src/targets/get_missing_info.R) sums up all recorded individual abstaining votes using the `switch()` function on every row where [`ballot_info_raw$typeid`](#ballot_info_rawtypeid) equals `4`. The results of a considerable share of ballots are recorded only using [a – Danish – character string](#ballot_results_ftcomment) instead of in a list of votes. In these cases, the number of abstentions is extracted with [`clean_ballot_results()`](/src/targets/clean_ballot_results.R) using the `strex` package and then added to the number of abstaining votes from the first step.

The maximum value stored in `ft_abstention` is `r max(ballot_results_ft$ft_abstention, na.rm = TRUE)` and the minimum value stored in `ft_abstention` is `r min(ballot_results_ft$ft_abstention, na.rm = TRUE)`. As the total number of MPs in Folketinget is 179, the value of `ft_abstention` cannot be greater than `179`.

```{r}
head(ballot_results_ft$ft_abstention)
```

#### ballot_results_ft\$ft_absent {#ballot_results_ftft_absent}

In `ft_absent`, the number of MPs who were absent for each ballot is stored as `r class(ballot_results_ft$ft_absent)` variable with values of the type `r typeof(ballot_results_ft$ft_absent)`. Since the record keeping of Folketinget is inconsistent regarding the coding of ballot results, values for this variable are calculated by substracting `ft_for`, `ft_against` and `ft_abstention` from `179`, the total number of MPs in Folketinget, using [`clean_ballot_results()`](/src/targets/clean_ballot_results.R).

The maximum value stored in `ft_absent` is `89` and the minimum value stored in `ft_absent` is `r min(ballot_results_ft$ft_absent, na.rm = TRUE)`. As the total number of MPs in Folketinget is 179, the value of `ft_absent` cannot be greater than `179`.

```{r}
head(ballot_results_ft$ft_absent)
```

#### ballot_results_ft\$ft_process_id {#ballot_results_ftft_process_id}

All legislative processes in Folketinget are assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each process ID is thus a unique identifier for one process relating to legislation in Folketinget. All IDs are stored as values of the type `r typeof(ballot_results_ft$ft_process_id)` as `r class(ballot_results_ft$ft_process_id)` variable.

This variable corresponds to the [`sagstrinid`](#ballot_info_rawsagstrinid) variable and the `Sagstrin` resource in [the Folketing online database](https://oda.ft.dk).

`ft_process_id` used to join [`ballot_topics_raw`](#ballot_topics_raw) to [`northatlantic_ft`](#northatlantic_ft).

```{r}
head(ballot_results_ft$ft_process_id)
```

#### ballot_results_ft\$ballot_nr {#ballot_results_ftballot_nr}

In addition to the [`ballot_id`](#ballot_results_ftballot_id), all ballot procedures in Folketinget are also assigned a number by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each ballot number is thus another identifier for one ballot in Folketinget. All ballot numbers are stored as values of the type `r typeof(ballot_results_ft$ballot_nr)` as `r class(ballot_results_ft$ballot_nr)` variable.

This variable corresponds to the [`ballot_info_raw$nummer`](#ballot_info_rawnummer) variable in the `Afstemning` resource in [the Folketing online database](https://oda.ft.dk). Take care not to confuse `ballot_nr` with [`ballot_id`](#ballot_results_ftballot_id).

```{r}
head(ballot_results_ft$ballot_nr)
```

#### ballot_results_ft\$ballot_type_id {#ballot_results_ftballot_type_id}

All ballot procedures in Folketinget are categorised using numeric values that correspond to the type of ballot (@tbl-ballottypeid). All Ballot Type IDs are stored as values of the type `r typeof(ballot_results_ft$ballot_type_id)` as `r class(ballot_results_ft$ballot_type_id)` variable.

| ID | Type | English | n |
|:-----------------|:-----------------|:------------------|-----------------:|
| 1 | Endelig vedtagelse | Final Adoption | `r length(ballot_results_ft$ballot_type_id[ballot_results_ft$ballot_type_id == "1"])` |
| 2 | Udvalgsindstilling | Committee Recommendation Report | `r length(ballot_results_ft$ballot_type_id[ballot_results_ft$ballot_type_id == "2"])` |
| 3 | Forslag til vedtagelse | Proposed Adoption | `r length(ballot_results_ft$ballot_type_id[ballot_results_ft$ballot_type_id == "3"])` |
| 4 | Ændringsforslag | Amendment | `r length(ballot_results_ft$ballot_type_id[ballot_results_ft$ballot_type_id == "4"])` |

: Ballot Type IDs as used by Folketingets Open Data Service {#tbl-ballottypeid} {.striped .hover}

This variable corresponds to `typeid` variable in [`ballot_info_raw`](#ballot_info_rawtypeid) and the `type` variable in the `Afstemningstype` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
head(ballot_results_ft$ballot_type_id)
```

#### ballot_results_ft\$comment {#ballot_results_ftcomment}

If necessary, comments on each ballot are stored as values of the type `r typeof(ballot_results_ft$comment)` in Danish language. A Folketing wording standard for `comment` does not seem to exist, so the sentence structures and vocabulary differs a lot between observations. As per `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`, there are `r sum(!is.na(ballot_results_ft$comment))` observations with comments (total number of observations: `r nrow(ballot_results_ft)`). Comments on ballot results mostly regard human or technical errors, for example:

| Danish | English |
|--------------------------------|----------------------------------------|
| Ved en fejl er der ikke registreret stemmeafgivning fra X’ plads. | By mistake, no vote was registeret at X’ seat. |
| Ved en fejl stemte X for/imod/hverken for eller imod forslaget. | By mistake, X voted for/against/neither for nor against the proposal. |
| Ved en fejl har X ikke fået stemt. | By mistake, X could not vote. |
| Ved en fejl fik X ikke afgivet sin stemme. | By mistake, X could not cast a vote. |
| Ved en fejl er Xs stemme registeret i Ys navn. | By mistake, X’ vote was registered as a vote by Y. |
| X stemte ved en fejl fra Y’s plads. | By mistake, X voted from Y’s seat. |
| 10 i X stemte ved en fejl for/imod/hverken for eller imod forslaget. | By mistake, 10 MPs from party X voted for/against/neither for nor against the proposal. |
| Ved en fejl er der registreret en stemme på X. | By mistake, a vote by X was recorded. |
| X undlod ved en fejl at stemme. | By mistake, X did not cast a vote. |
| Omafstemning | Voting Repeated |

: {.striped .hover}

```{r}
head(ballot_results_ft$comment)
```

#### ballot_results_ft\$ballot_result_string {#ballot_results_ftballot_result_string}

In `ballot_result_string`, ballot results are stored as values of the type `r typeof(ballot_results_ft$ballot_result_string)` in Danish language. The variable indicates whether the proposal was adopted or not; how many votes were in favor resp. against or abstentions, and from which political parties these votes came. A Folketing wording standard for `ballot_result_string` does not seem to exist, so the sentence structures and vocabulary differs a lot between observations.

As per `r format(file.info(here("data", "processed", "ballot_results_ft.rds"))$mtime, "%B %Y")`, there are `r sum(!is.na(ballot_results_ft$ballot_result_string))` observations with result character strings (total number of observations: `r nrow(ballot_results_ft)`). For the observations where `ballot_result_string` is not `NA`, the values are used to calculate [`ft_for`](#ballot_results_ftft_for), [`ft_against`](#ballot_results_ftft_against) and [`ft_abstention`](#ballot_results_ftft_abstention). Information on absent MPs is not provided in `ballot_result_string` but [can be inferred from the other values](#ballot_results_ftft_absent).

```{r}
str(ballot_results_ft$ballot_result_string)
```

------------------------------------------------------------------------

### ballot_info_raw {#ballot_info_raw}

`ballot_info_raw` is provided as `csv` file in `/data/raw/`. It contains the downloaded data on voting records before any preprocessing. The [processed data](#ballot_results_ft) is available as `rds` file in `/data/processed`. As per `r format(file.info(here("data", "processed", "northatlantic_votes.rds"))$mtime, "%B %Y")`, `ballot_info_raw.csv` contains `r nrow(ballot_info_raw)` observations of `r ncol(ballot_info_raw)` variables.

```{r}
head(ballot_info_raw)
```

Descriptions of all variables in `ballot_info_raw` are provided in the following sections.

#### ballot_info_raw\$id {#ballot_info_rawid}

See [ballot_result_ft\$ballot_id](#ballot_results_ftballot_id). Take care not to confuse `id` with [`nummer`](#ballot_info_rawnummer). In the raw data, `id` is stored as `r typeof(ballot_info_raw$id)` value.

```{r}
head(ballot_info_raw$id)
```

#### ballot_info_raw\$nummer {#ballot_info_rawnummer}

See [ballot_results_ft\$ballot_nr](#ballot_results_ftballot_nr). Take care not to confuse `nummer` with [`id`](#ballot_info_rawid). In the raw data, `nummer` is stored as `r typeof(ballot_info_raw$nummer)` value.

```{r}
head(ballot_info_raw$nummer)
```

#### ballot_info_raw\$konklusion

See [ballot_results_ft\$ballot_result_string](#ballot_results_ftballot_result_string). In the raw data, `konklusion` is stored as `r typeof(ballot_info_raw$konklusion)` value.

```{r}
head(ballot_info_raw$konklusion)
```

#### ballot_info_raw\$vedtaget {#ballot_info_rawvedtaget}

See [ballot_results_ft\$ballot_pass](#ballot_results_ftballot_pass). In the raw data, `vedtaget` is stored as `r typeof(ballot_info_raw$vedtaget)` value.

```{r}
head(ballot_info_raw$vedtaget)
```

#### ballot_info_raw\$kommentar

See [ballot_results_ft\$comment](#ballot_results_ftcomment). In the raw data, `kommentar` is stored as `r typeof(ballot_info_raw$kommentar)` value.

```{r}
head(ballot_info_raw$kommentar)
```

#### ballot_info_raw\$mødeid {#ballot_info_rawmødeid}

See [ballot_results_ft\$meeting_id](#ballot_results_ftmeeting_id). In the raw data, `mødeid` is stored as `r typeof(ballot_info_raw$mødeid)` value.

```{r}
head(ballot_info_raw$mødeid)
```

#### ballot_info_raw\$typeid {#ballot_info_rawtypeid}

See [ballot_results_ft\$ballot_type_id](#ballot_results_ftballot_type_id). In the raw data, `typeid` is stored as `r typeof(ballot_info_raw$typeid)` value.

```{r}
head(ballot_info_raw$typeid)
```

#### ballot_info_raw\$sagstrinid {#ballot_info_rawsagstrinid}

See [ballot_results_ft\$ft_process_id](#ballot_results_ftft_process_id). In the raw data, `sagstrinid` is stored as `r typeof(ballot_info_raw$sagstrinid)` value.

```{r}
head(ballot_info_raw$sagstrinid)
```

#### ballot_info_raw\$opdateringsdato

For all records kept in [the Folketing online database](https://oda.ft.dk), the time stamp of its last update is stored in `opdateringsdato`. All dates are stored as values of the type `r typeof(ballot_info_raw$opdateringsdato)`. The time stamps are formatted as `%Y-%m-%dT%T`, with some values even at split second level.

This variable is eliminated from [`ballot_results_ft`](#ballot_results_ft) as a result of data processing.

```{r}
head(ballot_info_raw$opdateringsdato)
```

------------------------------------------------------------------------

### ballot_topics_raw {#ballot_topics_raw}

`ballot_topics_raw` is provided as `csv` file in `/data/raw/`. It contains information on the content of each ballot in this data set, including the content of the proposal at hand. As per `r format(file.info(here("data", "raw", "ballot_topics_raw.csv"))$mtime, "%B %Y")`, `ballot_topics_raw.csv` contains `r nrow(ballot_topics_raw)` observations of `r ncol(ballot_topics_raw)` variables.

```{r}
head(ballot_topics_raw)
```

Descriptions of all variables in `ballot_topics_raw` are provided in the following sections.

#### ballot_topics_raw\$ft_process_id

All legislative processes in Folketinget are assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data). Each process ID is thus a unique identifier for one process relating to legislation in Folketinget. All IDs are stored as values of the type `r typeof(ballot_topics_raw$ft_process_id)` as `r class(ballot_topics_raw$ft_process_id)` variable.

This variable corresponds to the [`sagstrinid`](#ballot_info_rawsagstrinid) variable and the `Sagstrin` resource in [the Folketing online database](https://oda.ft.dk).

`ft_process_id` is used to join `ballot_topics_raw` to [`northatlantic_ft`](#northatlantic_ft) based on matching with[`ballot_results_ft$ft_process_id`](#ballot_results_ftft_process_id).

```{r}
head(ballot_topics_raw$ft_process_id)
```

#### ballot_topics_raw\$ft_process_step {#ballot_topicsrawft_process_step}

All legislative processes in Folketinget run their course through Folketinget in several steps which is described by `ft_process_step`. Process steps are stored as values of the type `r typeof(ballot_topics_raw$ft_process_step)` in Danish language.

This variable corresponds to the `titel` variable in the `Sagstrin` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
head(ballot_topics_raw$ft_process_step)
```

#### ballot_topics_raw\$ft_topic_id {#ballot_topicsrawft_topic_id}

Each proposal that is being voted on in Folketinget is assigned an ID by [Folketingets åbne data service (ODA)](https://www.ft.dk/dokumenter/aabne_data) based on the proposal's topic. Each topic ID is thus a unique identifier for one topic relating to several ballots and debates etc. in Folketinget. This identifier is stored in `ft_topic_id`. Topic IDs are stored as values of the type `r typeof(ballot_topics_raw$ft_topic_id)`.

This variable corresponds to the `id` variable in the `Sag` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
head(ballot_topics_raw$ft_topic_id)
```

#### ballot_topics_raw\$ft_topic {#ballot_topicsrawft_topic}

Each proposal that is being voted on in Folketinget has a description of the topic(s) that are mentioned in the proposal. This description is stored in `ft_topic`. Topic descriptions are stored as values of the type `r typeof(ballot_topics_raw$ft_topic)`.

This variable corresponds to the `titel` variable in the `Sag` resource in [the Folketing online database](https://oda.ft.dk).

```{r}
head(ballot_topics_raw$ft_topic)
```

------------------------------------------------------------------------

### cabinets_fo {#cabinets_fo}

`cabinets_fo` is provided as both `rds` file in `/data/processed` and `csv` file in `/data/processed/csv`. It contains information on the coalition governments of the Faroe Islands (Landsstýri), in particular a timeline including the parties that are part of each cabinet. As per `r format(file.info(here("data", "processed", "csv", "cabinets_fo.csv"))$mtime, "%B %Y")`, `cabinets_fo` contains information on `r nrow(cabinets_fo)` cabinets stored in `r ncol(cabinets_fo)` variables. This data set spans the timeframe covered by the voting database -- from `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")` until the last update of this data set on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`.

See also [cabinets_gl](#cabinets_gl) and [cabinets_dk](#cabinets_dk).


```{r}
head(cabinets_fo)
```

Descriptions of all variables in `cabinets_fo` are provided in the following sections.

#### cabinets_fo\$cabinet {#cabinets_focabinet}

Each cabinet formed in the Faroe Islands (Landsstýri) is assigned a human-readable identifier. The cabinets are usually named after the head of government, using their surname(s), followed by an integer number for multiple cabinets headed by the same person. Because in the timeframe covered by this data set, there have been two Faroese governments with a PM named Johannesen, the first letter of their first name is also appended to the `cabinet` variable. This variable is stored as value of the type `r typeof(cabinets_fo$cabinet)` as `r class(cabinets_fo$cabinet)` variable.

```{r}
head(cabinets_fo$cabinet)
```

#### cabinets_fo\$wikidata_id {#cabinets_fowikidata_id}

The `wikidata_id` variable stores the `QID` linking to the Wikidata entity representing the cabinet in question, making it easy to retrieve additional information from Wikidata, if necessary. This variable is stored as value of the type `r typeof(cabinets_fo$wikidata_id)` as `r class(cabinets_fo$wikidata_id)` variable.

```{r}
head(cabinets_fo$wikidata_id)
```

#### cabinets_fo\$location {#cabinets_folocation}

`location` indicates where a cabinet is formed -- in the Faroe Islands (`FO`). This variable is stored as value of the type `r typeof(cabinets_fo$location)` as `r class(cabinets_fo$location)` variable. When merging data, this proved to be helpful to distinguish between the different political parties, some of which share a common abbreviation across regions.

```{r}
table(cabinets_fo$location)
```

#### cabinets_fo\$start {#cabinets_fostart}

The date on which each cabinet is formed is stored as `r class(cabinets_fo$start)` variable of the type `r typeof(cabinets_fo$start)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_fo$start), "%B %d, %Y")` (`r min(cabinets_fo$start)`) and the most recent entry from `r format(max(cabinets_fo$start), "%B %d, %Y")` (`r max(cabinets_fo$start)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_fo.csv"))$mtime, "%B %Y")`.

```{r}
head(cabinets_fo$start)
```

#### cabinets_fo\$end {#cabinets_fo_end}

The date on which each cabinet is succeeded by the next one is stored as `r class(cabinets_fo$end)` variable of the type `r typeof(cabinets_fo$end)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_fo$end), "%B %d, %Y")` (`r min(cabinets_fo$end)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_fo.csv"))$mtime, "%B %Y")`.

Note that this date does not necessarily correspond to the date when a government 'collapses' or officially announces its resignation. Rather, the date denotes the day of the transition of power to the next cabinet.

```{r}
head(cabinets_fo$start)
```

#### cabinets_fo\$FO_A {#cabinets_fofoa}

`FO_A` indicates whether the Faroese political party **Fólkaflokkurin** (`A`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_A)` as `r class(cabinets_fo$FO_A)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_A` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_A)
```

#### cabinets_fo\$FO_B {#cabinets_fofob}

`FO_B` indicates whether the Faroese political party **Sambandsflokkurin** (`B`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_B)` as `r class(cabinets_fo$FO_B)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_B` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_B)
```

#### cabinets_fo\$FO_C {#cabinets_fofoc}

`FO_C` indicates whether the Faroese political party **Javnaðarflokkurin** (`C`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_C)` as `r class(cabinets_fo$FO_C)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_C` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_C)
```

#### cabinets_fo\$FO_D {#cabinets_fofod}

`FO_D` indicates whether the Faroese political party **Sjálvstýri** (`D`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_D)` as `r class(cabinets_fo$FO_D)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_D` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_D)
```

#### cabinets_fo\$FO_E {#cabinets_fofoe}

`FO_E` indicates whether the Faroese political party **Tjóðveldi** (`E`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_E)` as `r class(cabinets_fo$FO_E)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_E` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_E)
```

#### cabinets_fo\$FO_F {#cabinets_fofof}

`FO_F` indicates whether the Faroese political party **Framsókn** (`F`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_F)` as `r class(cabinets_fo$FO_F)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_F` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_F)
```

#### cabinets_fo\$FO_H {#cabinets_fofoh}

`FO_H` indicates whether the Faroese political party **Miðflokkurin** (`H`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_fo$FO_H)` as `r class(cabinets_fo$FO_H)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `FO_H` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_fo$FO_H)
```

------------------------------------------------------------------------

### cabinets_gl {#cabinets_gl}

`cabinets_gl` is provided as both `rds` file in `/data/processed` and `csv` file in `/data/processed/csv`. It contains information on the coalition governments of Greenland (Naalakersuisut), in particular a timeline including the parties that are part of each cabinet. As per `r format(file.info(here("data", "processed", "csv", "cabinets_gl.csv"))$mtime, "%B %Y")`, `cabinets_gl` contains information on `r nrow(cabinets_gl)` cabinets stored in `r ncol(cabinets_gl)` variables. This data set spans the timeframe covered by the voting database -- from `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")` until the last update of this data set on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`.

See also [cabinets_fo](#cabinets_fo) and [cabinets_dk](#cabinets_dk).

```{r}
head(cabinets_gl)
```

Descriptions of all variables in `cabinets_gl` are provided in the following sections.

#### cabinets_gl\$cabinet {#cabinets_glcabinet}

Each cabinet formed in Greenland (Naalakkersuisut) is assigned a human-readable identifier. The cabinets are usually named after the head of government, using their surname(s), followed by an integer number for multiple cabinets headed by the same person. Because in the timeframe covered by this data set, there have been two Faroese governments with a PM named Johannesen, the first letter of their first name is also appended to the `cabinet` variable. This variable is stored as value of the type `r typeof(cabinets_gl$cabinet)` as `r class(cabinets_gl$cabinet)` variable.

```{r}
head(cabinets_gl$cabinet)
```

#### cabinets_gl\$wikidata_id {#cabinets_glwikidata_id}

The `wikidata_id` variable stores the `QID` linking to the Wikidata entity representing the cabinet in question, making it easy to retrieve additional information from Wikidata, if necessary. This variable is stored as value of the type `r typeof(cabinets_gl$wikidata_id)` as `r class(cabinets_gl$wikidata_id)` variable.

```{r}
head(cabinets_gl$wikidata_id)
```

#### cabinets_gl\$location {#cabinets_gllocation}

`location` indicates where a cabinet is formed -- in Greenland (`GL`). This variable is stored as value of the type `r typeof(cabinets_gl$location)` as `r class(cabinets_gl$location)` variable. When merging data, this proved to be helpful to distinguish between the different political parties, some of which share a common abbreviation across regions.

```{r}
table(cabinets_gl$location)
```

#### cabinets_gl\$start {#cabinets_glstart}

The date on which each cabinet is formed is stored as `r class(cabinets_gl$start)` variable of the type `r typeof(cabinets_gl$start)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_gl$start), "%B %d, %Y")` (`r min(cabinets_gl$start)`) and the most recent entry from `r format(max(cabinets_gl$start), "%B %d, %Y")` (`r max(cabinets_gl$start)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_gl.csv"))$mtime, "%B %Y")`.

```{r}
head(cabinets_gl$start)
```

#### cabinets_gl\$end {#cabinets_glend}

The date on which each cabinet is succeeded by the next one is stored as `r class(cabinets_gl$end)` variable of the type `r typeof(cabinets_gl$end)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_gl$end), "%B %d, %Y")` (`r min(cabinets_gl$end)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_gl.csv"))$mtime, "%B %Y")`.

Note that this date does not necessarily correspond to the date when a government 'collapses' or officially announces its resignation. Rather, the date denotes the day of the transition of power to the next cabinet.

```{r}
head(cabinets_gl$start)
```

#### cabinets_gl\$GL_A {#cabinets_glgla}

`GL_A` indicates whether the Greenlandic political party **Atassut** (`A`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_A)` as `r class(cabinets_gl$GL_A)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_A` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_A)
```

#### cabinets_gl\$GL_D {#cabinets_glgld}

`GL_D` indicates whether the Greenlandic political party **Demokraatit** (`D`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_D)` as `r class(cabinets_gl$GL_D)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_D` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_D)
```

#### cabinets_gl\$GL_IA {#cabinets_glglia}

`GL_IA` indicates whether the Greenlandic political party **Inuit Ataqatigiit** (`IA`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_IA)` as `r class(cabinets_gl$GL_IA)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_IA` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_IA)
```

#### cabinets_gl\$GL_KP {#cabinets_glglkp}

`GL_KP` indicates whether the Greenlandic political party **Kattusseqatigiit Partiiat** (`KP`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_KP)` as `r class(cabinets_gl$GL_KP)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_KP` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_KP)
```

#### cabinets_gl\$GL_N {#cabinets_glgln}

`GL_N` indicates whether the Greenlandic political party **Naleraq** (`N`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_N)` as `r class(cabinets_gl$GL_N)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_N` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_N)
```

#### cabinets_gl\$GL_NQ {#cabinets_glglnq}

`GL_NQ` indicates whether the Greenlandic political party **Nunatta Qitornai** (`NQ`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_NQ)` as `r class(cabinets_gl$GL_NQ)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_NQ` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_NQ)
```

#### cabinets_gl\$GL_PI {#cabinets_glglpi}

`GL_PI` indicates whether the Greenlandic political party **Partii Inuit** (`PI`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_PI)` as `r class(cabinets_gl$GL_PI)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_PI` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_PI)
```

#### cabinets_gl\$GL_SIU {#cabinets_glglsiu}

`GL_SIU` indicates whether the Greenlandic political party **Siumut** (`SIU`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_gl$GL_SIU)` as `r class(cabinets_gl$GL_SIU)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `GL_SIU` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_gl$GL_SIU)
```

------------------------------------------------------------------------

### cabinets_dk {#cabinets_dk}

`cabinets_dk` is provided as `csv` and `rds` file in `/data/processed/`. It contains information on coalition governments of Denmark, in particular a timeline including the parties that are part of each cabinet. As per `r format(file.info(here("data", "processed", "csv", "cabinets_dk.csv"))$mtime, "%B %Y")`, `cabinets_dk` contains information on `r nrow(cabinets_dk)` cabinets stored in `r ncol(cabinets_dk)` variables. On this list are `r sum(cabinets_dk$bloc == "left", na.rm = TRUE)` red bloc/left-wing, `r sum(cabinets_dk$bloc == "right", na.rm = TRUE)` blue/right-wing and `r sum(cabinets_dk$bloc == "across", na.rm = TRUE)` cross-bloc cabinets. This data set spans the timeframe covered by the voting database -- from `r format(min(northatlantic_ft$ballot_date), "%B %d, %Y")` until the last update of this data set on `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %d, %Y")`.

See also [cabinets_fo](#cabinets_fo) and [cabinets_gl](#cabinets_gl).

```{r}
head(cabinets_dk)
```

Descriptions of all variables in `cabinets_dk` are provided in the following sections.

#### cabinets_dk\$cabinet {#cabinets_dkcabinet}

Each cabinet formed in Denmark is assigned a human-readable identifier. The cabinets are usually named after the head of government, using their surname(s), followed by an integer number for multiple cabinets headed by the same person. Because in the timeframe covered by this data set, there have been two Danish governments with a PM named Rasmussen, the first letter of their first name is also appended to the `cabinet` variable. This variable is stored as value of the type `r typeof(cabinets_dk$cabinet)` as `r class(cabinets_dk$cabinet)` variable.

```{r}
head(cabinets_dk$cabinet)
```

#### cabinets_dk\$wikidata_id {#cabinets_dkwikidata_id}

The `wikidata_id` variable stores the `QID` linking to the Wikidata entity representing the cabinet in question, making it easy to retrieve additional information from Wikidata, if necessary. This variable is stored as value of the type `r typeof(cabinets_dk$wikidata_id)` as `r class(cabinets_dk$wikidata_id)` variable.

```{r}
head(cabinets_dk$wikidata_id)
```

#### cabinets_dk\$bloc {#cabinets_dkbloc}

`bloc` indicates whether a cabinet belongs to either the red/left or blue/right section of the political spectrum or if it is formed across both blocs. This variable is stored as value of the type `r typeof(cabinets_dk$bloc)` as `r class(cabinets_dk$bloc)` variable.

```{r}
table(cabinets_dk$bloc)
```

#### cabinets_dk\$type {#cabinets_dktype}

`type` indicates whether a cabinet is formed by a single politial party or if it is a coalition government. This variable is stored as value of the type `r typeof(cabinets_dk$type)` as `r class(cabinets_dk$type)` variable.

Note that a `single_party` cabinet does not necessarily have the majority of seats in parliament. The cabinet in question may instead rely on informal support agreements with other political parties that are not officially part of the cabinet.

```{r}
table(cabinets_dk$type)
```

#### cabinets_dk\$start {#cabinets_dkstart}

The date on which each cabinet is formed is stored as `r class(cabinets_dk$start)` variable of the type `r typeof(cabinets_dk$start)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_dk$start), "%B %d, %Y")` (`r min(cabinets_dk$start)`) and the most recent entry from `r format(max(cabinets_dk$start), "%B %d, %Y")` (`r max(cabinets_dk$start)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_dk.csv"))$mtime, "%B %Y")`.

```{r}
head(cabinets_dk$start)
```

#### cabinets_dk\$end {#cabinets_dkend}

The date on which each cabinet is succeeded by the next one is stored as `r class(cabinets_dk$end)` variable of the type `r typeof(cabinets_dk$end)`. Calendar information is formatted as `%Y-%m-%d`, the earliest entry being from `r format(min(cabinets_dk$end), "%B %d, %Y")` (`r min(cabinets_dk$end)`) as of `r format(file.info(here("data", "processed", "csv", "cabinets_dk.csv"))$mtime, "%B %Y")`.

Note that this date does not necessarily correspond to the date when a government 'collapses' or officially announces its resignation. Rather, the date denotes the day of the transition of power to the next cabinet.

```{r}
head(cabinets_dk$start)
```

#### cabinets_dk\$DK_A {#cabinets_dkdka}

`DK_A` indicates whether the Danish political party **Socialdemokratiet** (`A`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_A)` as `r class(cabinets_dk$DK_A)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_A` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_A)
```

#### cabinets_dk\$DK_B {#cabinets_dkdkb}

`DK_B` indicates whether the Danish political party **Radikale Venstre** (`B`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_B)` as `r class(cabinets_dk$DK_B)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_B` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_B)
```

#### cabinets_dk\$DK_C {#cabinets_dkdkc}

`DK_C` indicates whether the Danish political party **Det Konservative Folkeparti** (`C`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_C)` as `r class(cabinets_dk$DK_C)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_C` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_C)
```

#### cabinets_dk\$DK_F {#cabinets_dkdkf}

`DK_F` indicates whether the Danish political party **Socialistisk Folkeparti** (`F`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_F)` as `r class(cabinets_dk$DK_F)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_F` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_F)
```

#### cabinets_dk\$DK_I {#cabinets_dkdki}

`DK_I` indicates whether the Danish political party **Liberal Alliance** (`I`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_I)` as `r class(cabinets_dk$DK_I)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_I` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_I)
```

#### cabinets_dk\$DK_M {#cabinets_dkdkm}

`DK_M` indicates whether the Danish political party **Moderaterne** (`M`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_M)` as `r class(cabinets_dk$DK_M)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_M` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_M)
```

#### cabinets_dk\$DK_V {#cabinets_dkdkv}

`DK_V` indicates whether the Danish political party **Venstre** (`V`) is member of the cabinet. This variable is stored as value of the type `r typeof(cabinets_dk$DK_V)` as `r class(cabinets_dk$DK_V)` variable.

Note that a cabinet may rely on more political parties/MPs to maintain a majority. These situations are not reflected in `DK_V` which only stores statements on official cabinet membership.

```{r}
summary(cabinets_dk$DK_V)
```

------------------------------------------------------------------------

### northatlantic_ft {#northatlantic_ft}

`northatlantic_ft` is the resulting product of the [targets pipeline](/_targets.R) and is provided as both `rds` file in `/data/processed` and `csv` file in `/data/processed/csv`. It contains data on voting records of the MPs specified in [`MP_names`](#mp_names), created by processing and joining [`ballot_results_ft`](#ballot_results_ft), [`northatlantic_votes`](#northatlantic_votes), [`ballot_topics_raw`](#ballot_topics_raw) and [`cabinets_fo_gl`](#cabinets_fo_gl). As per `r format(file.info(here("data", "processed", "northatlantic_ft.rds"))$mtime, "%B %Y")`, `northatlantic_ft` contains `r nrow(northatlantic_ft)` observations of `r ncol(northatlantic_ft)` variables.

```{r}
str(northatlantic_ft)
```

Descriptions of all variables in `northatlantic_ft` are provided in the following sections.

#### northatlantic_ft\$ballot_id

`ballot_id` is created by using [`join_results()`](/src/targets/join_results.R) on `northatlantic_votes` and `ballot_results_ft`. See [`northatlantic_votes$ballot_id`](#northatlantic_votesballot_id).

```{r}
str(northatlantic_ft$ballot_id)
```

#### northatlantic_ft\$MP_id

`MP_id` is created by using [`join_results()`](/src/targets/join_results.R) on `northatlantic_votes` and `ballot_results_ft`. See [`northatlantic_votes$MP_id`](#northatlantic_votesmp_id).

```{r}
str(northatlantic_ft$MP_id)
```

#### northatlantic_ft\$surname

`surname` is created by using [`join_results()`](/src/targets/join_results.R) on `northatlantic_votes`, `ballot_results_ft`, and `MP_names`. See [`MP_names$surname`](#mp_namessurname).

```{r}
str(northatlantic_ft$surname)
```

#### northatlantic_ft\$origin

`origin` is created by using [`join_results()`](/src/targets/join_results.R) on `northatlantic_votes`, `ballot_results_ft`, and `MP_names`. See [`MP_names$origin`](#mp_namesorigin).

```{r}
summary(northatlantic_ft$origin)
```

#### northatlantic_ft\$party

`party` is created by using [`join_results()`](/src/targets/join_results.R) on `northatlantic_votes`, `ballot_results_ft`, and `MP_names`. See [`MP_names$party`](#mp_namesparty).

```{r}
summary(northatlantic_ft$party)
```

#### northatlantic_ft\$gvt_party_at_home

`gvt_party_at_home` is created by using [`join_results()`](/src/targets/join_results.R) on `northatlantic_votes`, `ballot_results_ft`, `MP_names` and `cabinets_fo` resp. `cabinets_gl`, indicating whether the MP is a member of a political party that is part of the governing Naalakkersuisut (GL) resp. Landsstýri (FO) at the time. See [`cabinets_fo`](#cabinets_fo) and [`cabinets_gl`](#cabinets_gl).

```{r}
summary(northatlantic_ft$gvt_party_at_home)
```

#### northatlantic_ft\$vote_type_id

`northatlantic_ft` is a result of [`join_results()`](/src/targets/join_results.R) in which `vote_type_id` is joined from `northatlantic_votes$vote_type_id`. See [`northatlantic_votes$vote_type_id`](#northatlantic_votesvote_type_id).

```{r}
str(northatlantic_ft$vote_type_id)
```

#### northatlantic_ft\$vote_id

See [`northatlantic_votes$votes_id`](#northatlantic_votesvote_id).

```{r}
str(northatlantic_ft$vote_id)
```

#### northatlantic_ft\$ballot_pass

See [`ballot_results_ft$ballot_pass`](#ballot_results_ftballot_pass).

```{r}
str(northatlantic_ft$ballot_pass)
```

#### northatlantic_ft\$ft_process_step

See [`ballot_topics_raw$ft_process_step`](#ballot_topics_rawft_process_step).

```{r}
str(northatlantic_ft$ft_process_step)
```

#### northatlantic_ft\$ft_topic_id

See [`ballot_topics_raw$ft_topic_id`](#ballot_topics_rawft_topic_id).

```{r}
str(northatlantic_ft$ft_topic_id)
```

#### northatlantic_ft\$ft_topic

See [`ballot_topics_raw$ft_topic`](#ballot_topics_rawft_topic).

```{r}
str(northatlantic_ft$ft_topic)
```

#### northatlantic_ft\$ft_for

See [`ballot_results_ft$ft_for`](#ballot_results_ftft_for).

```{r}
str(northatlantic_ft$ft_for)
```

#### northatlantic_ft\$ft_against

See [`ballot_results_ft$ft_against`](#ballot_results_ftft_against).

```{r}
str(northatlantic_ft$ft_against)
```

#### northatlantic_ft\$ft_abstention

See [`ballot_results_ft$ft_abstention`](#ballot_results_ftft_abstention).

```{r}
str(northatlantic_ft$ft_abstention)
```

#### northatlantic_ft\$ft_absent

See [`ballot_results_ft$ft_absent`](#ballot_results_ftft_absent).

```{r}
str(northatlantic_ft$ft_absent)
```

#### northatlantic_ft\$ballot_date

See [`ballot_results_ft$ballot_date`](#ballot_results_ftballot_date).

```{r}
str(northatlantic_ft$ballot_date)
```

#### northatlantic_ft\$ballot_type_id

See [`ballot_results_ft$ballot_type_id`](#ballot_results_ftballot_type_id).

```{r}
str(northatlantic_ft$ballot_type_id)
```

#### northatlantic_ft\$gvt_type_dk

`gvt_type_dk` is created by using [`join_results()`](/src/targets/join_results.R) on `cabinets_dk`, indicating whether the Danish government is a coalition or a single-party government at the time of the observation. See [`cabinets_dk$type`](#cabinets_dktype).

```{r}
summary(northatlantic_ft$gvt_type_dk)
```

#### northatlantic_ft\$gvt_bloc_dk

`gvt_bloc_dk` is created by using [`join_results()`](/src/targets/join_results.R) on `cabinets_dk`, indicating the political bloc (left/red, right/blue or across) the Danish government belongs to at the time of the observation. See [`cabinets_dk$bloc`](#cabinets_dkbloc).

```{r}
summary(northatlantic_ft$gvt_bloc_dk)
```

#### northatlantic_ft\$comment

See [`ballot_results_ft$comment`](#ballot_results_ftcomment).

```{r}
str(northatlantic_ft$comment)
```

#### northatlantic_ft\$ballot_result_string

See [`ballot_results_ft$ballot_result_string`](#ballot_results_ftballot_result_string).

```{r}
str(northatlantic_ft$ballot_result_string)
```